### 2014-08-25 anglais/paper.tex
add original english paper

\documentclass{article}
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
\usepackage[english]{babel}
\usepackage{titling}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{scrextend}
\changefontsizes[20pt]{12pt}
\usepackage{floatrow}
\usepackage{courier}
\usepackage{caption}
\usepackage{fontspec}
\setmonofont{DejaVu Sans Mono}
\title{Paper 2014 - A talk about Network}
\author{Daniel Maxime (Group 2326)}
\date{August 2014}

\begin{document}
\maketitle
\newpage

\tableofcontents
\clearpage

%
% Like most people we, English lecturers, use computer networks every day.
% We have a vague understanding of what IP addresses are, but what do they refer to exactly?
% There has been a lof a talk about IPv4, IPv6 and even IPv8 more recently.
% What are they? What are the differences?
% 
% Why do we need to mention « ports » in addition to « addresses » ?
% What’s the link between such « ports » and the notion of « service » ?
% Could you give some common examples ?
% 
% Last time we inadvertently opened a network configuration window,
% we came across the word "subnet mask": what is is, and what is it used for?
% 
% Is the subnet mask anything to do with routers?
% Isn't a router a computer ? Or is it the same as a switch?
%

\section{Introduction}
	\subsection{Computers network}

	Computers that we all know are useful for a lot a things: manage works, compute for science research,
	make movies, graohics, play games, ... But computers are more usefull when then can communicate with other !
	On top of all that, they can connect their users between them. That's probably the most important part of a
	computer nowadays. Interacting with computers is usefull but using it remotly or contacting services which
	is on the other side of the earth, it's just beautiful.

	The computer networks have undergone major changes over time. Multiple projects came out and
	only some of them (a single one in fact) survived. Let's see how this works...

	\subsection{A brief history}

	At first, to communicate with a computer system, you need a common way to "talk" with the others. To achieve
	this, some projects were made to try to unify the system with performance and well minded.

	The communication schema and definition (most of the time, this is public and accessible freely, under what we
	call, some RFC (Request For Comments)) used on computer science are call "Protocols".
	Some of them were made to connect computers between them: ARCnet, Ethernet, Token Ring, IP, ...

	These protocols were made for the same purpose (connect physically and logically devices) but with differents
	working method, the main difference is the way "how and when devices can talk".
	ARCnet and Token Ring uses "tokens" to allow someone to talk or not, Ethernet (which is the most used now)
	talk when he want and manage collisions (when two people talk on the same time).

	I'll only keep protocols which are still used nowadays, everywhere, and skip the others.
	But, how these protocols works togethers ?

\section{Network layers}

	The perk of the network base is the "OSI model" (Open Systems Interconnection model) which characterizes and
	standardizes the internal functions of a communication system. All "internet" network uses it. This model split
	the works with 7 layers, each independant of one another. You can changer a layer without affecting the content
	of the others. It's due to this method that you can browse the web on wireless or wired connection, without change
	all your hardware.

	Let me explain these layers from the bottom to the top, to understand how each small protocol used on internet
	works together to provide a full and flexible support. After that, we will see how theses protocols interacts
	with others.

	\subsection{Layer 1 - Physical layer}

	This layer is definitively the easiest layer of the OSI model, it's globally just the wire which connect one
	device to another (your computer to your Internet Provider's box, the Internet Provider's box to their
	data center, etc). In your house, except "ethernet-cable" or wireless access, you probably don't have
	any other layer 1 technology, but there are many other.

	Now, we have a cable between two devices, that's fine, but how can I make it communicate ?
	With the layer 2 of course.

	\subsection{Layer 2 - Data link layer}

	This (single) layer permits to devices to communicate together, on a small area (eg: devices you have at your house,
	nothing more). The most common protocol used at this layer is Ethernet. This protocol is made to tramsit data
	over the layer 1, with some collisions and errors detection. After that, to connect two devices bewteen them, you
	need to use addresses. Ethernet use MAC addresses.
	\footnote{No, you don't need to have an "Apple Mac Computer" to have a MAC address.
	All physical ethernet network cards got a unique one on the world.}
	\footnote{Exemple of MAC address: 00:54:77:65:78:21}
	A MAC address is 48 bits longs, that's means that there are about 281,000 billion address possible. I think that's
	suffisant for your home (yes, remimber, this protocol connects only a small area).

	This protocol, like all protocols (you will see later) use a generic data representation:
	header + payload (+ footer).
	The footer is not always present on protocols, but often, this is where is put "checksum" (a small amount of data
	wihich enables corruption detection).

	The header is dedicated for Ethernet, the payload is simply used to put
	the layer 3 on it. This method is called "encapsulation" (like Matriochka), it's with this method that all layers
	will be put together.

	To communicate with someone, we must know it's address, but when we talk to someone, it's a good idea to
	get it's response. To help it to respond, we will provide our address too. Well, the header will contains
	at least the destination address and the source (our) address. This will be the same for all protocols
	that we'll see.

	Now we can connect two devices and exchanges data (on the payload) between them. Let's see how we can extends
	the area of communication (internet on your home only it's not very interresting).

	\subsection{Layer 3 - Network layer}

	To extends your connectivity all around the world, using MAC address only is not possible due to conception
	on the protocol: ethernet, as I said is made for local traffic. To extends this traffic to the outside, we need
	to use another protocol, which is made for that. We called IP (Internet Protocol). Yes, this is really the protocol
	which is really used to have "Internet".

	Nice, but, what is IP exactly ? IP is the protocol which permits to make the link with the underlaying layer
	and global mapped address. IP uses... IP address
	\footnote{Exemple of IP address: 82.212.175.9} to represents source and destination. For the v4 of the protocol
	(commonly called IPv4), address are 32 bits long, which make about 4 billions unique address. For the begening of
	the "Internet time", this was absolutly huge.

	One more time, we will encapsulate this protocol on the underlaying protocol. We have this schema right now:
	\begin{center}
	\includegraphics[scale=0.3]{content/layer3.eps}
	\end{center}

	We can now contact devices outside our home. We will see later how and why it's only now that we can contact
	the "outside world". But that's nice, but how can I contact a specific service (web browser, file transfert, chat, ...)
	on a specific device, we only know it's address right now.

	\subsection{Layer 4 - Transport layer}

	To understand un little bit more how that's works, I'll draw an analogy with real life. Imagine a world with
	road and a lot of buildings with flats. Roads it's the layer 1 (wire), your car is layer 2 (etnernet), the building
	address, flat stage and flat number is described by the IP address. Now you are at your destination, you want to
	go to a specific location on this flat. When your enter the flat, you are in the lobby, you have multiple doors
	in front of you. That's the solution. Behind each doors you have one service.

	Theses doors on network are called "ports".

	This happen on layer 4 with multiple possibe protocols. The most used are TCP and UDP. They are both the same purpose
	and differents ports, but works in two way differents, these way are not important to understand how it works.

	Just keep in mind that these ports enable you to access specific services on the remote device. Like each time,
	this works with encapsulation. That's what we have after this encapsulation:
	\begin{center}
	\includegraphics[scale=0.3]{content/layer4.eps}
	\end{center}

	Like before, the header contains the source port and the destination port. Yes, you have a source port. In fact,
	a webserver is a service behind a door, but your web browser is a service too, behind a door at your home.
	That's explain how you can browser multiple differents website at the same times: everythings has it's own door (port).

	And voila. You can communicate and exchange data with your correspondant ! But, what kind of data ?

	\subsection{Layer 7 - Application layer}

	We are now at layer 7. What ? And what about layer 5 and 6 ? They are not important for us, we can skip it, most
	of the times, these layer are not used at all because we don't need them.

	Well, what's is the layer 7 ? It's simply data you want to exchange. You can send "hello" (really just "hello"),
	and that's what the remote service (remember, door) will receive. That's easy but, to request a web page for exemple,
	we must provide a comprehensive way to talk with the web server. To perform that's correctly, we use... one more time,
	protocols ! At this layer, we found a lot of protocols: http, ftp, ssh, irc, telnet, smtp, pop3, imap, ...

	Each of these protocols have a default port number. The exact content of the protocol is describe on each RFC
	specially written for that.

	Now, our complete frame look like that:
	\begin{center}
	\includegraphics[scale=0.3]{content/layer7.eps}
	\end{center}

	That's nice, but why do we need all of these protocols to reach the wanted destination, and why have we split that ?
	To understand that's, we must go deeper in the description.

\section{A little deeper...}
	You have (I hope) the schema with building, flats and roads on your mind. Keep it fresh, I'll complete it to well
	understand some devices and specific additionnal services you can find on networks.

	For specific reasons, flats can communicate with layer 2 with the same floor only (you have probably 3 or 4 flats
	per stages). To communicate between flats, we need to connect them to each other, for that we will use a "switch".
	This device's job is just to send traffic (based on destination MAC address) on the right wire connected.

	To communicate with your building (without go outside your building I mean), you need to connect each stages between
	them. You can use switch to connects each switch between them (that's pretty easy no ?). Each flat has it's own
	IP address, and to segments all the Internet IP Address, we will split it per building. Each building has it's own
	part of "The Internet (IP)". This part is called "subnet". With this feature, you can communicate with your building
	without additionnal devices or something else. You are isolated.

	To make building communucate with others, you need to put a device on the building door, which will works on the
	link between the building and the road. To access some roads and know which road take, we use a devices
	which know these road... or more precisely, these routes ! These devices are called... router. Easy not ?

	The job of a router is just to connect your sub-network with others.

	One interresting thing that we can put on the building too, is a security agent. We can put one on the router, to
	control who enter and go out the building, and we can put a security agent on each flat, to control who comes in, 
	trying to access some services. If this security agent see someone not autorised, it will simply throw it out.
	This security agent is called "firewall".

	That's all folk ! You now know basiclly how a computer network works. Pretty simple, no ? That's how it works
	nowadays, but computer science is a science which progress each days, and the futur is already concidered.

\section{What's next ?}
	Remember you, I explained you layer 3 with "IP" version 4 (IPv4). Nowadays, IPv6 exists. In fact, IPv4 with it's
	32 bits long for address is too short now. We are really close to reach the limit of existing address, that's the
	main reason for IPv6 to exists. The main new think that IPv6 improve is the address no more on 32 bits,
	but on 128 bits. That put the limits at about approximately 3.4x$10^{38}$ addresses. This is really really big.
	This is not the only one change with IPv6, some technical details changes too. IPv4 is more than 30 years old, 
	since this time, we found and improved IPv6 with some missing or some deprecated features.

	To enable everyone to have IPv6 at their home, the world must use a software IPv6-capable. But the avantage of
	layerd system is that we must only change layer 3 of the whole system, the other layers remain unchanged. That means
	that HTTP, TCP and Ethernet still works the same way on IPv4 or IPv6. That's so beautiful !

	Finally, if you heard of IPv8, IPv9 or something like that, forget it, they doesn't exists. Simply.

\section{Conclusion}
	You now know how computers networks (Internet mainly) works, with which protocols and how they communicate each other.
	Your network cards contains a MAC address used by IP to go outside your house. You have ports which specify service
	and the application protocol which contains your requests for specific services.

	\newpage

\section{Sources}
	\begin{itemize}
		\itemsep0em
		\item https://en.wikipedia.org/wiki/Ethernet
		\item https://en.wikipedia.org/wiki/Internet\_Protocol
		\item https://en.wikipedia.org/wiki/MAC\_address
		\item https://en.wikipedia.org/wiki/ARCnet
		\item https://en.wikipedia.org/wiki/TokenRing
		\item https://en.wikipedia.org/wiki/OSI\_model
		\item Graphics are made using https://draw.io
	\end{itemize}

\end{document}

### 2014-08-25 anglais/paper.tex
add corrections from Celine Eppe

@@
 
-	Computers that we all know are useful for a lot a things: manage works, compute for science research,
-	make movies, graohics, play games, ... But computers are more usefull when then can communicate with other !
+	Computers that we all know are useful for a lot of things: managing works, computing for science research,
+	making movies, graphics, playing games, ... But computers are more useful when then can communicate with each other !
 	On top of all that, they can connect their users between them. That's probably the most important part of a
-	computer nowadays. Interacting with computers is usefull but using it remotly or contacting services which
-	is on the other side of the earth, it's just beautiful.
+	computer nowadays. Interacting with computers is useful but using it remotly or contacting a service that
+	is on the other side of the Earth, that's just beautiful.
 
 	The computer networks have undergone major changes over time. Multiple projects came out and
-	only some of them (a single one in fact) survived. Let's see how this works...
+	only some of them (a single one in fact) survived. Let's see how it works...
 
@@
 
-	The communication schema and definition (most of the time, this is public and accessible freely, under what we
-	call, some RFC (Request For Comments)) used on computer science are call "Protocols".
+	The communication schema and definition (most of the time, this is public and freely accessible under what we
+	call RFC (Request For Comments)) used on computer science are called "Protocols".
 	Some of them were made to connect computers between them: ARCnet, Ethernet, Token Ring, IP, ...
 
-	These protocols were made for the same purpose (connect physically and logically devices) but with differents
-	working method, the main difference is the way "how and when devices can talk".
-	ARCnet and Token Ring uses "tokens" to allow someone to talk or not, Ethernet (which is the most used now)
-	talk when he want and manage collisions (when two people talk on the same time).
+	These protocols were made for the same purpose (connect physically and logically devices) but with different
+	working methods. The main difference is the way "how and when devices can talk".
+	ARCnet and Token Ring use "tokens" to allow someone to talk or not, Ethernet (which is the most used now)
+	talks when he wants and manages collisions (when two people talk at the same time).
 
 	I'll only keep protocols which are still used nowadays, everywhere, and skip the others.
-	But, how these protocols works togethers ?
+	But, how these protocols work together ?
 
@@
 
-	The perk of the network base is the "OSI model" (Open Systems Interconnection model) which characterizes and
-	standardizes the internal functions of a communication system. All "internet" network uses it. This model split
-	the works with 7 layers, each independant of one another. You can changer a layer without affecting the content
-	of the others. It's due to this method that you can browse the web on wireless or wired connection, without change
+	The mot important part of the network base is the "OSI model" (Open Systems Interconnection model) which characterizes and
+	standardizes the internal functions of a communication system. All "Internet" networks use it. This model splits
+	the work in 7 layers, each independant from one another. You can changer a layer without affecting the content
+	of the others. It's due to this method that you can browse the web on wireless or wired connection without changing
 	all your hardware.
 
-	Let me explain these layers from the bottom to the top, to understand how each small protocol used on internet
-	works together to provide a full and flexible support. After that, we will see how theses protocols interacts
-	with others.
+	Let me explain these layers from the bottom to the top, to understand how each small protocol used on the Internet
+	works with the others to provide a full and flexible support. After that, we will see how these protocols interact
+	with each other.
 
@@
 
-	This layer is definitively the easiest layer of the OSI model, it's globally just the wire which connect one
+	This layer is definitely the easiest layer of the OSI model, it's globally just the wire which connects one
 	device to another (your computer to your Internet Provider's box, the Internet Provider's box to their
-	data center, etc). In your house, except "ethernet-cable" or wireless access, you probably don't have
-	any other layer 1 technology, but there are many other.
+	data center, etc). In your house, except the "ethernet-cable" or the wireless access, you probably don't have
+	any other layer 1 technology, but there are many others.
 
-	Now, we have a cable between two devices, that's fine, but how can I make it communicate ?
+	Now, we have a cable between two devices, that's fine, but how can we make them communicate ?
 	With the layer 2 of course.
@@
 
-	This (single) layer permits to devices to communicate together, on a small area (eg: devices you have at your house,
-	nothing more). The most common protocol used at this layer is Ethernet. This protocol is made to tramsit data
-	over the layer 1, with some collisions and errors detection. After that, to connect two devices bewteen them, you
+	This (single) layer enables devices to communicate together on a small area (eg: devices you have at your house,
+	nothing more). The most common protocol used at this layer is Ethernet. This protocol is made to transmit data
+	over the layer 1, with some collisions and errors detection. After that, to connect two devices between them, you
 	need to use addresses. Ethernet use MAC addresses.
 	\footnote{No, you don't need to have an "Apple Mac Computer" to have a MAC address.
-	All physical ethernet network cards got a unique one on the world.}
+	All physical ethernet network cards have got a unique one on the world.}
 	\footnote{Exemple of MAC address: 00:54:77:65:78:21}
-	A MAC address is 48 bits longs, that's means that there are about 281,000 billion address possible. I think that's
-	suffisant for your home (yes, remimber, this protocol connects only a small area).
+	A MAC address is 48 bits longs, that means that there are about 281,000 billion addresses possible. I think that's
+	enough for your home (yes, remember, this protocol connects only a small area).
 
-	This protocol, like all protocols (you will see later) use a generic data representation:
+	This protocol, like all protocols (you will see later) uses a generic data representation:
 	header + payload (+ footer).
-	The footer is not always present on protocols, but often, this is where is put "checksum" (a small amount of data
-	wihich enables corruption detection).
+	The footer is not always present on every protocol, but often, this is where the "checksum" (a small amount of data
+	which enables corruption detection) is put.
 
 	The header is dedicated for Ethernet, the payload is simply used to put
-	the layer 3 on it. This method is called "encapsulation" (like Matriochka), it's with this method that all layers
+	the layer 3 on it. This method is called "encapsulation" (like Matriochka dolls), it's with this method that all layers
 	will be put together.
 
-	To communicate with someone, we must know it's address, but when we talk to someone, it's a good idea to
-	get it's response. To help it to respond, we will provide our address too. Well, the header will contains
-	at least the destination address and the source (our) address. This will be the same for all protocols
+	To communicate with someone, we must know their address, but when we talk to someone, it's a good idea to
+	get their response. To help them respond, we will provide our address too. Well, the header will contain
+	at least the destination address and the source address (ours). This will be the same for all the protocols
 	that we'll see.
 
-	Now we can connect two devices and exchanges data (on the payload) between them. Let's see how we can extends
-	the area of communication (internet on your home only it's not very interresting).
+	Now we can connect two devices and exchange data (on the payload) between them. Let's see how we can extend
+	the area of communication (Internet in your home only is not very interesting).
 
@@
 
-	To extends your connectivity all around the world, using MAC address only is not possible due to conception
-	on the protocol: ethernet, as I said is made for local traffic. To extends this traffic to the outside, we need
-	to use another protocol, which is made for that. We called IP (Internet Protocol). Yes, this is really the protocol
+	To extend your connectivity all around the world, using MAC addresses only is not possible due to conception
+	of the protocol: Ethernet, as I said is made for local traffic. To extends this traffic to the outside, we need
+	to use another protocol, which is made for that. It's called IP (Internet Protocol). Yes, this is the protocol
 	which is really used to have "Internet".
 
-	Nice, but, what is IP exactly ? IP is the protocol which permits to make the link with the underlaying layer
-	and global mapped address. IP uses... IP address
-	\footnote{Exemple of IP address: 82.212.175.9} to represents source and destination. For the v4 of the protocol
-	(commonly called IPv4), address are 32 bits long, which make about 4 billions unique address. For the begening of
-	the "Internet time", this was absolutly huge.
+	Nice, but, what exactly is IP ? IP is the protocol which enables to make the link with the underlying layer
+	and global mapped address. IP uses... IP addresses.
+	\footnote{Exemple of IP address: 82.212.175.9} to represents source and destination. With the fourth version of the protocol
+	(commonly called IPv4), addresses are 32 bits long, which makes about 4 billions unique addresses. At the beginning of
+	the "Internet time", this was absolutely huge.
 
-	One more time, we will encapsulate this protocol on the underlaying protocol. We have this schema right now:
+	One more time, we will encapsulate this protocol on the underlying protocol. We have this schema right now:
 	\begin{center}
@@
 	We can now contact devices outside our home. We will see later how and why it's only now that we can contact
-	the "outside world". But that's nice, but how can I contact a specific service (web browser, file transfert, chat, ...)
-	on a specific device, we only know it's address right now.
+	the "outside world". That's nice, but how can I contact a specific service (web browser, file transfert, chat, ...)
+	on a specific device, we only know its address right now.
 
@@
 
-	To understand un little bit more how that's works, I'll draw an analogy with real life. Imagine a world with
-	road and a lot of buildings with flats. Roads it's the layer 1 (wire), your car is layer 2 (etnernet), the building
-	address, flat stage and flat number is described by the IP address. Now you are at your destination, you want to
+	To understand a little bit more how that works, I'll draw an analogy with real life. Imagine a world with
+	roads and a lot of buildings with flats. Roads are the layer 1 (wire), your car is the layer 2 (Ethernet), the building
+	address, flat stage and flat number are described by the IP address. Now you are at your destination, you want to
 	go to a specific location on this flat. When your enter the flat, you are in the lobby, you have multiple doors
@@
 
-	Theses doors on network are called "ports".
+	These doors on network are called "ports".
 
-	This happen on layer 4 with multiple possibe protocols. The most used are TCP and UDP. They are both the same purpose
-	and differents ports, but works in two way differents, these way are not important to understand how it works.
-
+	This happen on layer 4 with multiple possible protocols. The most used are TCP and UDP. They are both the same purpose
+	and differents ports, but work in two different ways, these ways are not important to understand how it works.
+	ss
 	Just keep in mind that these ports enable you to access specific services on the remote device. Like each time,
@@
 	Like before, the header contains the source port and the destination port. Yes, you have a source port. In fact,
-	a webserver is a service behind a door, but your web browser is a service too, behind a door at your home.
-	That's explain how you can browser multiple differents website at the same times: everythings has it's own door (port).
+	a webserver is a service behind a door and your web browser is a service too, but behind a door at your home.
+	That explains how you can browse multiple and different websites at the same time: everything has its own door (port).
 
-	And voila. You can communicate and exchange data with your correspondant ! But, what kind of data ?
+	And voila. You can communicate and exchange data with your correspondant ! But what kind of data ?
 
@@
 
-	We are now at layer 7. What ? And what about layer 5 and 6 ? They are not important for us, we can skip it, most
-	of the times, these layer are not used at all because we don't need them.
+	We are now at layer 7. What ? And what about layer 5 and 6 ? They are not important for us, we can skip them, most
+	of the time, these layers are not used at all because we don't need them.
 
-	Well, what's is the layer 7 ? It's simply data you want to exchange. You can send "hello" (really just "hello"),
-	and that's what the remote service (remember, door) will receive. That's easy but, to request a web page for exemple,
-	we must provide a comprehensive way to talk with the web server. To perform that's correctly, we use... one more time,
-	protocols ! At this layer, we found a lot of protocols: http, ftp, ssh, irc, telnet, smtp, pop3, imap, ...
+	Well, what is the layer 7 ? It's simply data you want to exchange. You can send "hello" (really just "hello"),
+	and that's what the remote service (remember, the door) will receive. That's easy but to request a web page for example,
+	we must provide a comprehensive way to talk with the web server. To perform that correctly, we use... one more time,
+	protocols ! At this layer, we find a lot of protocols: http, ftp, ssh, irc, telnet, smtp, pop3, imap, ...
 
-	Each of these protocols have a default port number. The exact content of the protocol is describe on each RFC
+	Each of these protocols has a default port number. The exact content of the protocol is described on each RFC
 	specially written for that.
 
-	Now, our complete frame look like that:
+	Now, our complete frame looks like that:
 	\begin{center}
@@
 
-	That's nice, but why do we need all of these protocols to reach the wanted destination, and why have we split that ?
-	To understand that's, we must go deeper in the description.
+	That's nice, but why do we need all of these protocols to reach the wanted destination, and why do we split them?
+	To understand that, we must go deeper in the description.
 
 \section{A little deeper...}
-	You have (I hope) the schema with building, flats and roads on your mind. Keep it fresh, I'll complete it to well
-	understand some devices and specific additionnal services you can find on networks.
+	You have (I hope) the schema with building, flats and roads on your mind. Keep it fresh, I'll complete it to 
+	understand well some devices and specific additionnal services you can find on networks.
 
-	For specific reasons, flats can communicate with layer 2 with the same floor only (you have probably 3 or 4 flats
-	per stages). To communicate between flats, we need to connect them to each other, for that we will use a "switch".
-	This device's job is just to send traffic (based on destination MAC address) on the right wire connected.
+	For specific reasons, flats can communicate with layer 2 at the same floor only (you have probably 3 or 4 flats
+	per stages). To communicate between flats, we need to connect them to each other. For that we will use a "switch".
+	This device's job is just to send traffic (based on the destination MAC address) on the right wire connected.
 
-	To communicate with your building (without go outside your building I mean), you need to connect each stages between
-	them. You can use switch to connects each switch between them (that's pretty easy no ?). Each flat has it's own
-	IP address, and to segments all the Internet IP Address, we will split it per building. Each building has it's own
+	To communicate with your building (without going outside your building I mean), you need to connect each stages between
+	them. You can use a switch to connect the stages between them (that's pretty easy right ?). Each flat has its own
+	IP address, and to segments all the Internet IP Addresses, we will split them per building. Each building has its own
 	part of "The Internet (IP)". This part is called "subnet". With this feature, you can communicate with your building
@@
 
-	To make building communucate with others, you need to put a device on the building door, which will works on the
-	link between the building and the road. To access some roads and know which road take, we use a devices
-	which know these road... or more precisely, these routes ! These devices are called... router. Easy not ?
+	To make buildings communicate with others, you need to put a device on the building door, which will work on the
+	link between the building and the road. To access some roads and know which road to take, we use a device
+	which knows these road... or more precisely, these routes ! This device is called... a router. Easy right ?
 
@@
 
-	One interresting thing that we can put on the building too, is a security agent. We can put one on the router, to
-	control who enter and go out the building, and we can put a security agent on each flat, to control who comes in, 
-	trying to access some services. If this security agent see someone not autorised, it will simply throw it out.
+	Another interesting thing that we can put on the building is a security agent. We can put one on the router to
+	control who enters and goes out the building, and we can put a security agent on each flat, to control who comes in, 
+	trying to access some services. If this security agent sees someone unauthorized, he will simply throw them out.
 	This security agent is called "firewall".
 
-	That's all folk ! You now know basiclly how a computer network works. Pretty simple, no ? That's how it works
-	nowadays, but computer science is a science which progress each days, and the futur is already concidered.
+	That's all folks ! You now know basically how a computer network works. Pretty simple, right ? That's how it works
+	nowadays, but computer science is a science which progresses everyday and the futur is already considered.
 
 \section{What's next ?}
-	Remember you, I explained you layer 3 with "IP" version 4 (IPv4). Nowadays, IPv6 exists. In fact, IPv4 with it's
-	32 bits long for address is too short now. We are really close to reach the limit of existing address, that's the
-	main reason for IPv6 to exists. The main new think that IPv6 improve is the address no more on 32 bits,
-	but on 128 bits. That put the limits at about approximately 3.4x$10^{38}$ addresses. This is really really big.
-	This is not the only one change with IPv6, some technical details changes too. IPv4 is more than 30 years old, 
-	since this time, we found and improved IPv6 with some missing or some deprecated features.
+	Remember, I explained to you the layer 3 with the fourth version of "IP" (IPv4). Nowadays, IPv6 exists. In fact, the
+	IPv4's 32 bits long addresses are too short now. We'll reach the limit of existing addresses very soon, that's the
+	main reason for IPv6 to exists. The main new thing that IPv6 improves is that the addresses are no more on 32 bits,
+	but on 128 bits. That puts the limit at approximately 3.4x$10^{38}$ addresses. This is really really big.
+	This is not the only one change with IPv6, some technical details change too. IPv4 is more than 30 years old, 
+	since then, we found and improved IPv6 with some missing or some deprecated features.
 
-	To enable everyone to have IPv6 at their home, the world must use a software IPv6-capable. But the avantage of
-	layerd system is that we must only change layer 3 of the whole system, the other layers remain unchanged. That means
-	that HTTP, TCP and Ethernet still works the same way on IPv4 or IPv6. That's so beautiful !
+	To enable everyone to have IPv6 at their home, the world must use a software IPv6-capable. But the avantage of a
+	layered system is that we only need to change the layer 3 in the whole system, the other layers remain unchanged. That means
+	that HTTP, TCP and Ethernet still work the same way on IPv4 or IPv6. That's so beautiful !
 
-	Finally, if you heard of IPv8, IPv9 or something like that, forget it, they doesn't exists. Simply.
+	Finally, if you've heard of IPv8, IPv9 or something like that, forget it, they simply don't exist.
+	\newpage
 
 \section{Conclusion}
-	You now know how computers networks (Internet mainly) works, with which protocols and how they communicate each other.
-	Your network cards contains a MAC address used by IP to go outside your house. You have ports which specify service
+	You now know how computers networks (Internet mainly) works, with which protocols and how they communicate with each other.
+	Your network card contains a MAC address used by IP to go outside your house. You have ports which specify the service
 	and the application protocol which contains your requests for specific services.

### 2014-08-25 anglais/paper.tex
improve paper

@@
 \begin{document}
-\maketitle
+
+\begin{titlepage}
+\begin{center}
+\textsc{\LARGE Haute Ecole de la Province de Liège}\\[0.5cm]
+\textsc{\Large Catégorie technique}\\[4cm]
+
+% Title
+\huge \bfseries A talk about computer networks \\
+\textsc{\Large by Daniel Maxime, 2326}\\[2cm]
+
+% Author and supervisor
+\textsc{\large Course: Langue Moderne}
+
+\textsc{\large Lecturer: Véronique Randaxhe}
+
+\vfill
+{\large August 25, 2014}
+
+\end{center}
+\end{titlepage}
 \newpage
@@
 \section{Introduction}
+
 	\subsection{Computers network}
@@
 	The computer networks have undergone major changes over time. Multiple projects came out and
-	only some of them (a single one in fact) survived. Let's see how it works...
+	only some of them survived. Let's see how it works...
 
@@
 
-	The mot important part of the network base is the "OSI model" (Open Systems Interconnection model) which characterizes and
+	The most important part of the network base is the "OSI model" (Open Systems Interconnection model) which characterizes and
 	standardizes the internal functions of a communication system. All "Internet" networks use it. This model splits
@@
 	of the others. It's due to this method that you can browse the web on wireless or wired connection without changing
-	all your hardware.
+	all your hardware/software.
 
@@
 	nothing more). The most common protocol used at this layer is Ethernet. This protocol is made to transmit data
-	over the layer 1, with some collisions and errors detection. After that, to connect two devices between them, you
+	over the layer 1, with some errors detection. After that, to connect two devices between them, you
 	need to use addresses. Ethernet use MAC addresses.
@@
 	All physical ethernet network cards have got a unique one on the world.}
-	\footnote{Exemple of MAC address: 00:54:77:65:78:21}
-	A MAC address is 48 bits longs, that means that there are about 281,000 billion addresses possible. I think that's
-	enough for your home (yes, remember, this protocol connects only a small area).
+	A MAC address is 48 bits longs\footnote{Exemple of MAC address: 00:54:77:65:78:21},
+	that means that there are about 281,000 billion addresses possible. I think that's enough for
+	your home (yes, remember, this protocol connects only a small area).
 
@@
 	Nice, but, what exactly is IP ? IP is the protocol which enables to make the link with the underlying layer
-	and global mapped address. IP uses... IP addresses.
+	and global mapped address. IP uses... IP addresses
 	\footnote{Exemple of IP address: 82.212.175.9} to represents source and destination. With the fourth version of the protocol
@@
 	\begin{center}
-	\includegraphics[scale=0.3]{content/layer3.eps}
+	\includegraphics[scale=0.35]{content/layer3.eps}
 	\end{center}
@@
 	address, flat stage and flat number are described by the IP address. Now you are at your destination, you want to
-	go to a specific location on this flat. When your enter the flat, you are in the lobby, you have multiple doors
+	go to a specific location on this flat. When you enter the flat, you are in the lobby, you have multiple doors
 	in front of you. That's the solution. Behind each doors you have one service.
@@
 	and differents ports, but work in two different ways, these ways are not important to understand how it works.
-	ss
 	Just keep in mind that these ports enable you to access specific services on the remote device. Like each time,
@@
 	\begin{center}
-	\includegraphics[scale=0.3]{content/layer4.eps}
+	\includegraphics[scale=0.35]{content/layer4.eps}
 	\end{center}
@@
 	we must provide a comprehensive way to talk with the web server. To perform that correctly, we use... one more time,
-	protocols ! At this layer, we find a lot of protocols: http, ftp, ssh, irc, telnet, smtp, pop3, imap, ...
+	protocols ! At this layer, we find a lot of protocols: http (for web pages), ftp (for file sharing),
+	ssh (remote console), irc (chat), telnet (remote console), smtp (sending mail), pop3 and imap (mail storage), ...
 
@@
 	\begin{center}
-	\includegraphics[scale=0.3]{content/layer7.eps}
+	\includegraphics[scale=0.35]{content/layer7.eps}
 	\end{center}
@@
 \section{A little deeper...}
+
 	You have (I hope) the schema with building, flats and roads on your mind. Keep it fresh, I'll complete it to 
@@
 
-	That's all folks ! You now know basically how a computer network works. Pretty simple, right ? That's how it works
+	That's all folks ! You now know (basically) how a computer network works. Pretty simple, right ? That's how it works
 	nowadays, but computer science is a science which progresses everyday and the futur is already considered.
@@
 \section{What's next ?}
+
 	Remember, I explained to you the layer 3 with the fourth version of "IP" (IPv4). Nowadays, IPv6 exists. In fact, the
@@
 	Finally, if you've heard of IPv8, IPv9 or something like that, forget it, they simply don't exist.
-	\newpage
 
 \section{Conclusion}
+
 	You now know how computers networks (Internet mainly) works, with which protocols and how they communicate with each other.
@@
 	and the application protocol which contains your requests for specific services.
+
+	\newpage
+
+\section{Glossary}
+
+	\begin{itemize}
+		\itemsep0em
+		\item \textbf{Protocols}:
+			specific method used to describe the mechanism, the fields of data, bits, bytes,
+			the order of operations and data to send and receive to make a working-communication.
+
+		\item \textbf{Internet Provider}: 
+			companies interconnected with other companies which enables you to reach different networks.
+			All of these different networks make "the Internet", it's simply a lot of interconnected-networks.
+
+		\item \textbf{Checksum}: 
+			a fast operation which consist of make the sum of the data with an algorythm more or less secure.
+			This mechanism enables protocol to know if the payload is altered or not by doing the same operation
+			and comparing the checksum value. Safer is the checksum, longer and slower it is.
+
+		\item \textbf{Data encapsulation}: 
+			the fact of put data on a larger container.
+
+		\item \textbf{Response mechanism}: 
+			when you receive data, you can response to it just by fill in the application payload
+			with your response, then swaping source and destination address on headers.
+
+		\item \textbf{Subnet}: 
+			each IP contained on the same subnets can communicate each other without router, a router
+			is the device that enables communication between multiple subnets.
+
+		\item \textbf{TCP}: 
+			protocol which enables "secure" connection with a negociation (handshake) before working. It provides
+			an acknowledgment and retransmission light but optimized system.
+
+		\item \textbf{UDP}: 
+			protocol less "secure" than TCP because it does not support retransmission, acknowledgment and handshake,
+			but is very smaller than TCP. This protocol is often used for multimedia content streaming.
+
+		\item \textbf{Switch}: 
+			devices that works on layer 2 only and forward frame on the right (destination address) physical port.
+
+		\item \textbf{Router}: 
+			interconnect multiple subnet and take decision for routing (best path, etc.)
+
+		\item \textbf{Firewall}: 
+			security software which analyze traffic and take decision based on users rules.
+
+	\end{itemize}
 
@@
 		\item https://en.wikipedia.org/wiki/OSI\_model
+		\item http://www.cisco.com/c/en/us/support/docs/ip/routing-information-protocol-rip/13769-5.html
 		\item Graphics are made using https://draw.io

### 2014-08-25 anglais/paper.tex
corrected version of paper

@@
 		\item \textbf{Protocols}:
-			specific method used to describe the mechanism, the fields of data, bits, bytes,
-			the order of operations and data to send and receive to make a working-communication.
+			specific methods used to describe the mechanism, the fields of data, bits, bytes,
+			the order of operations and data to send and receive to make a working communication.
 
 		\item \textbf{Internet Provider}: 
-			companies interconnected with other companies which enables you to reach different networks.
-			All of these different networks make "the Internet", it's simply a lot of interconnected-networks.
+			companies interconnected with other companies which enable you to reach different networks.
+			All of these different networks make "the Internet", it's simply a lot of interconnected networks.
 
 		\item \textbf{Checksum}: 
-			a fast operation which consist of make the sum of the data with an algorythm more or less secure.
-			This mechanism enables protocol to know if the payload is altered or not by doing the same operation
-			and comparing the checksum value. Safer is the checksum, longer and slower it is.
+			a fast operation which consists of making the sum of the data with an algorythm more or less secure.
+			This mechanism enables protocols to know if the payload is altered or not by doing the same operation
+			and comparing the checksum value. The safer the checksum is, the longer and slower it is.
 
 		\item \textbf{Data encapsulation}: 
-			the fact of put data on a larger container.
+			the act of putting data in a larger container.
 
 		\item \textbf{Response mechanism}: 
-			when you receive data, you can response to it just by fill in the application payload
-			with your response, then swaping source and destination address on headers.
+			when you receive data, you can response to it just by filling in the application payload
+			with your response, then swapping the source and the destination addresses on headers.
 
 		\item \textbf{Subnet}: 
-			each IP contained on the same subnets can communicate each other without router, a router
+			each IP contained on the same subnets can communicate with the others without a router, a router
 			is the device that enables communication between multiple subnets.
@@
 		\item \textbf{TCP}: 
-			protocol which enables "secure" connection with a negociation (handshake) before working. It provides
-			an acknowledgment and retransmission light but optimized system.
+			protocol which enables a "secure" connection with a negociation (handshake) before working. It provides
+			an acknowledgment and retransmission light but with an optimized system.
 
 		\item \textbf{UDP}: 
-			protocol less "secure" than TCP because it does not support retransmission, acknowledgment and handshake,
-			but is very smaller than TCP. This protocol is often used for multimedia content streaming.
+			protocol less "secure" than TCP because it doesn't support retransmission, acknowledgment and handshake,
+			but is much smaller than TCP. This protocol is often used for multimedia content streaming.
 
 		\item \textbf{Switch}: 
-			devices that works on layer 2 only and forward frame on the right (destination address) physical port.
+			devices that work on layer 2 only and forward frame on the right (destination address) physical port.
 
 		\item \textbf{Router}: 
-			interconnect multiple subnet and take decision for routing (best path, etc.)
+			interconnects multiple subnets and take decisions for routing (best path, etc.)
 
 		\item \textbf{Firewall}: 
-			security software which analyze traffic and take decision based on users rules.
+			security software which analyzes traffic and takes decisions based on the user's rules.
 

### 2014-08-25 design/petra 2/node/http/petraremote.js
add last project data, new versions, a lot of improvments

@@ -2,31 +2,35 @@ var PetraRemote = function() {
 	this.socket;
 	this.self = this;
 	
-	this.sensors = [
-		{code: 'L1', name: 'Cut-Out #1'},
-		{code: 'L2', name: 'Cut-Out #2'},
-		{code: 'T',  name: 'Epaisseur'},
-		{code: 'S',  name: 'Slot'},
-		{code: 'CS', name: 'Chariot stable'},
-		{code: 'AP', name: 'Bras'},
-		{code: 'PP', name: 'Plongeur'},
-		{code: 'DE', name: 'Bac d\'entrée'},
-	];
+	this.server = "syna";
+	this.port   = 8081;
 	
-	this.actuators = [
-		{code: 'CP', name: 'Position chariot'},
-		{code: 'C1', name: 'Convoyeur 1'},
-		{code: 'C2', name: 'Convoyeur 2'},
-		{code: 'PV', name: 'Ventouse'},
-		{code: 'PA', name: 'Plongeur'},
-		{code: 'AA', name: 'Bras'},
-		{code: 'GA', name: 'Grappin'},
+	this.buttons = [
+		// sensors
+		{type: 0, code: 'L1', name: 'Cut-Out #1', values: ["non", "oui"]},
+		{type: 0, code: 'L2', name: 'Cut-Out #2', values: ["non", "oui"]},
+		{type: 0, code: 'T',  name: 'Epaisseur',  values: ["0", "1"]},
+		{type: 0, code: 'S',  name: 'Slot',       values: ["non-présent", "présent"]},
+		{type: 0, code: 'CS', name: 'Chariot stable', values: ["instable", "stable"]},
+		{type: 0, code: 'AP', name: 'Bras',           values: ["tapis 1", "tapis 2"]},
+		{type: 0, code: 'PP', name: 'Plongeur',       values: ["levé", "baissé"]},
+		{type: 0, code: 'DE', name: 'Bac d\'entrée',  values: ["pas vide", "vide"]},
+		
+		// actuators
+		{type: 1, code: 'CP', name: 'Position chariot', values:
+			["bac d'entrée", "tapis 1", "tapis 2", "bac ko"]},
+		{type: 1, code: 'C1', name: 'Tapis 1',  values: ["arrêté", "en fonction"]},
+		{type: 1, code: 'C2', name: 'Tapis 2',  values: ["arrêté", "en fonction"]},
[…]

### 2014-08-25 design/petra 2/node/petra.js

@@ -22,10 +22,10 @@ app.listen(8080);
 
 /* root handler on new connection */
 function handler(connection) {
-	var petra_sensors_change = function(value) {
+	var petra_change = function(value) {
 		console.log("[+] Sending update to <" + connection.remoteAddress + ">");
 		connection.sendUTF(JSON.stringify({
-			event: "sensors-change",
+			event: "petra-change",
 			data: value
 		}));
 	};
@@ -43,13 +43,13 @@ function handler(connection) {
 		}
 	};
 	
-	petra.on('sensors-change', petra_sensors_change);
+	petra.on('petra-change', petra_change);
 	connection.on('message', connection_message);
 	
 	// removing each handlers listeners on close
 	connection.on('close', function() {
 		connection.removeAllListeners();	
-		petra.removeListener('sensors-change', petra_sensors_change);
+		petra.removeListener('petra-change', petra_change);
 	});
 }
 

### 2014-08-25 design/petra 2/node/petra.server.js

@@ -53,33 +53,26 @@ var PetraServer = function(host, port) {
 		
 		console.log(json);
 		
-		for(var i = 0; i < json.length; i++) 
-			this.sensors[i].value = json[i];
+		for(var i = 0; i < json[0].length; i++) 
+			this.sensors[i].value = json[0][i];
 		
-		this.emit('sensors-change', this.sensors);
+		for(var i = 0; i < json[1].length; i++) 
+			this.actuators[i].value = json[1][i];
+		
+		this.emit('petra-change', [this.sensors, this.actuators]);
 	};
 	
 	this.request = function(object, connection) {
 		// console.log(object);
 		
 		if(object.request == 'status') {
-			console.log('[+] Petra: sensors-status');
-			return this.sensors_status(connection);
-		}
-		
-		if(object.request == 'poweroff') {
-			console.log('[+] Petra: poweroff: ' + object.payload.sensors);
-			return this.sensors_poweroff(object.payload.sensors);
-		}
-		
-		if(object.request == 'poweron') {
-			console.log('[+] Petra: poweron: ' + object.payload.sensors);
-			return this.sensors_poweron(object.payload.sensors);
+			console.log('[+] Petra: status');
+			return this.petra_status(connection);
 		}
 		
 		if(object.request == 'toggle') {
-			console.log('[+] Petra: toggle: ' + object.payload.sensors);
-			return this.sensors_toggle(object.payload.sensors);
+			console.log('[+] Petra: toggle: ' + object.payload.port);
+			return this.actuators_toggle(object.payload.port);
 		}
 		
 		if(object.request == 'ping') {
@@ -90,10 +83,10 @@ var PetraServer = function(host, port) {
 		}
 	};
 	
-	this.sensors_status = function(connection) {
+	this.petra_status = function(connection) {
 		connection.sendUTF(JSON.stringify({
-			event: 'sensors-change',
-			data: this.sensors
+			event: 'petra-change',
+			data: [this.sensors, this.actuators]
 		}));
 	};
 	
@@ -103,26 +96,13 @@ var PetraServer = function(host, port) {
 				return i;
 	}
 	
-	this.actuators_poweroff = function(actuators) {
-		return this.actuators_change(this.actuators_get(actuators), 1);
-	};
-	
-	this.actuators_poweron = function(actuators) {
-		return this.actuators_change(this.actuators_get(actuators), 0);
-	};
-	
 	this.actuators_toggle = function(actuators) {
[…]

### 2014-08-25 design/petra 2/qnx/petrad.c

@@ -68,13 +68,14 @@ void dump_actuators(actuator_t *actuators) {
 
 void send_sensors(thread_data_t *data) {
 	char buffer[1024];
+	int offset;
 	
 	//
 	// building JSON pseudo-array
 	// this is not beautiful but faster than create a true JSON object
 	//
-	snprintf(buffer, sizeof(buffer),
-	         "[%d,%d,%d,%d,%d,%d,%d,%d]\n",
+	offset = snprintf(buffer, sizeof(buffer),
+	         "[[%d,%d,%d,%d,%d,%d,%d,%d],",
 	         data->sensors.L1,
 	         data->sensors.L2,
 	         data->sensors.T,
@@ -83,6 +84,17 @@ void send_sensors(thread_data_t *data) {
 	         data->sensors.AP,
 	         data->sensors.PP,
 	         data->sensors.DE
+	);
+	
+	snprintf(buffer + offset, sizeof(buffer) - offset,
+	         "[%d,%d,%d,%d,%d,%d,%d]]\n",
+	         data->actuators.CP,
+	         data->actuators.C1,
+	         data->actuators.C2,
+	         data->actuators.PV,
+	         data->actuators.PA,
+	         data->actuators.AA,
+	         data->actuators.GA
 	);
 	
 	if(send(data->sockfd, buffer, strlen(buffer), 0) < 0)
@@ -99,7 +111,6 @@ void *thread_sensors(void *_data) {
 	int fd;
 	
 	if((fd = open(SENSORS_FILENAME, O_RDONLY)) < 0)
-	// if((fd = open("/tmp/petra", O_RDONLY)) < 0)
 		diep("[-] sensors: open: " SENSORS_FILENAME);
 	
 	//
@@ -111,7 +122,7 @@ void *thread_sensors(void *_data) {
 	//
 	// initial read and send
 	//
-	if(read(fd, &data->sensors, 1) != 1)
+	if(read(fd, &data->sensors, sizeof(sensor_t)) != sizeof(sensor_t))
 		perror("[-] sensors: read");
 	
 	send_sensors(data);
@@ -123,7 +134,7 @@ void *thread_sensors(void *_data) {
 	while(1) {
 		lseek(fd, 0, SEEK_SET);
 		
-		if(read(fd, &data->sensors, 1) != 1)
+		if(read(fd, &data->sensors, sizeof(sensor_t)) != sizeof(sensor_t))
 			perror("[-] sensors: read");
 		
 		//
[…]

### 2014-08-25 design/petra 2/qnx/petrad.h

@@ -11,7 +11,7 @@
 		unsigned int PP :1;
 		unsigned int DE :1;
 		
-	} sensor_t;
+	} __attribute__ ((packed)) sensor_t;
 	
 	typedef struct actuator_t {
 		unsigned CP :2;
@@ -22,10 +22,15 @@
 		unsigned AA :1;
 		unsigned GA :1;
 		
-	} actuator_t;
+	} __attribute__ ((packed)) actuator_t;
 
-	#define SENSORS_FILENAME    "/dev/capteursPETRA"
-	#define ACTUATORS_FILENAME  "/dev/actuateursPETRA"
+	#ifdef __linux__
+		#define SENSORS_FILENAME    "/tmp/petra0"
+		#define ACTUATORS_FILENAME  "/tmp/petra1"
+	#else
+		#define SENSORS_FILENAME    "/dev/capteursPETRA"
+		#define ACTUATORS_FILENAME  "/dev/actuateursPETRA"
+	#endif
 	
 	#define SOCKET_PORT         8788
 	#define SOCKET_LISTEN       "0.0.0.0"

### 2014-08-25 design/scheduling/scheduling.c

@@ -1,0 +1,73 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+#include <pthread.h>
+#include <sched.h>
+#include <unistd.h>
+
+int yield = 0;
+
+void diep(char *str) {
+	perror(str);
+	exit(EXIT_FAILURE);
+}
+
+void *sporadic_thread(void *data) {
+	int z = 0;
+	
+	while(1) {
+		if(!z++)
+			printf("[+] loop for %p\n", data);
+		
+		if(yield)
+			sched_yield();
+	}
+	
+	return data;
+}
+
+int main(int argc, char *argv[]) {
+	pthread_attr_t attr;
+	struct sched_param param;
+	int i, limit = 1, period = 400;
+	
+	printf("[+] note: %s [threads = 1 [yield = off [period = 400]]]\n", argv[0]);
+	
+	if(argc > 3)
+		period = atoi(argv[3]);
+	
+	if(argc > 2)
+		yield = 1;
+	
+	if(argc > 1)
+		limit = atoi(argv[1]);
+	
+	printf("[+] starting with %d threads\n", limit);
+	printf("[+] yield %s\n", yield ? "enabled" : "disabled");
+
+	pthread_attr_init(&attr);
+	memset(&param, '\0', sizeof(param));
+
+	param.sched_priority        = sched_get_priority_max(SCHED_SPORADIC) / 2;
+	param.sched_ss_low_priority = sched_get_priority_min(SCHED_SPORADIC);
+	param.sched_ss_max_repl     = 20;
+	nsec2timespec(&param.sched_ss_repl_period, period * 1000000); // ms
+	nsec2timespec(&param.sched_ss_init_budget, 200 * 1000000); // 200 ms
+	
+	printf("[+] priority     : %d\n", param.sched_priority);
+	printf("[+] low priority : %d\n", param.sched_ss_low_priority);
+	printf("[+] replenishment: %d\n", param.sched_ss_max_repl);
+
+	pthread_attr_setschedparam(&attr, &param);		
+	pthread_attr_setschedpolicy(&attr, SCHED_SPORADIC);
+	pthread_attr_setinheritsched(&attr, PTHREAD_EXPLICIT_SCHED);
+
+	for(i = 0; i < limit; i++) {
+		if(pthread_create(NULL, &attr, sporadic_thread, (void *) i))
+			diep("[-] pthread_create");
+	}
+	
+	sleep(20);
+	
+	return 0;
+}

### 2014-08-25 reseau/arp-libnet/formater.c

@@ -1,0 +1,35 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+
+char *format_ipMD(unsigned char *data, char *str) {
+	unsigned int i;
+	char temp[8];
+	
+	*str = '\0';
+	
+	for(i = 0; i < 4;) {
+		sprintf(temp, "%d.", data[i++]);
+		strcat(str, temp);
+	}
+	
+	str[strlen(str) - 1] = '\0';
+	
+	return str;
+}
+
+char *format_macMD(unsigned char *data, char *str) {
+	unsigned int i;
+	char temp[8];
+	
+	*str = '\0';
+	
+	for(i = 0; i < 6;) {
+		sprintf(temp, "%02X:", data[i++]);
+		strcat(str, temp);
+	}
+	
+	str[strlen(str) - 1] = '\0';
+	
+	return str;
+}

### 2014-08-25 reseau/arp-libnet/formater.h

@@ -1,0 +1,6 @@
+#ifndef FORMATER_H
+	#define FORMATER_H
+	
+	char *format_ipMD(unsigned char *data, char *str);
+	char *format_macMD(unsigned char *data, char *str);
+#endif

### 2014-08-25 reseau/arp-libnet/labo-arp.c

@@ -1,0 +1,168 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <ctype.h>
+#include <libnet.h>
+#include <getopt.h>
+#include "formater.h"
+#include "macresolv.h"
+
+static struct option long_opts[] = {
+	{"target", required_argument, 0, 't'},
+	{"ip",     required_argument, 0, 'i'},
+	{"mac",    required_argument, 0, 'm'},
+	{0, 0, 0, 0}
+};
+
+void diefMD(char *str) {
+	fprintf(stderr, "[-] %s", str);
+	exit(EXIT_FAILURE);
+}
+
+void dienMD(libnet_t *libnet, char *str) {
+	fprintf(stderr, "[-] %s: %s\n", str, libnet_geterror(libnet));
+	exit(EXIT_FAILURE);
+}
+
+int usageMD(char *bin) {
+	fprintf(stderr, "Usage: %s --ip [spoof ip] --target [host ip] --mac [host mac]\n", bin);
+	return EXIT_FAILURE;
+}
+
+int attackMD(libnet_t *libnet, libnet_ptag_t tag, uint8_t *hostmac) {
+	u_int8_t *packet;
+	u_int32_t packet_s;
+	int i;
+	
+	if(tag == -1)
+		dienMD(libnet, "arp header");
+	
+	if((tag = libnet_autobuild_ethernet(hostmac, ETHERTYPE_ARP, libnet)) == -1)
+		dienMD(libnet, "ethernet header");
+	
+	if(libnet_adv_cull_packet(libnet, &packet, &packet_s) == -1)
+		dienMD(libnet, "packet");
+		
+	printf("[+] packet size: %u\n", packet_s);
+	
+	if((i = libnet_write(libnet)) == -1)
+		dienMD(libnet, "write");
+
+	printf("[+] %u bytes sent\n", i);
+	
+	return i;
+}
+
+int main(int argc, char *argv[]) {
+	libnet_t *libnet;
+	libnet_ptag_t tag;
+	
+	char *hostmac_resolv, *dip;
+	uint8_t *hostmac = NULL;
+	int hostmac_len;
+	struct libnet_ether_addr *localmac_net;
+	u_char localmac[ETH_ALEN];
+	
+	uint32_t localip;
+	
+	int32_t init_target = 0, init_host = 0;
+	u_char target[IP_ALEN], host[IP_ALEN];
+	
[…]

### 2014-08-25 reseau/arp-libnet/macresolv.c

@@ -1,0 +1,120 @@
+#include <stdio.h>
+#include <string.h>
+#include <stdlib.h>
+#include <stdint.h>
+#include <unistd.h>
+#include <sys/socket.h>
+#include <sys/ioctl.h>
+#include <linux/if_ether.h>
+#include <net/if.h>
+#include <netinet/in.h>
+#include <arpa/inet.h>
+#include <linux/ip.h>
+#include <linux/udp.h>
+#include <linux/tcp.h>
+#include <libnet.h>
+#include "macresolv.h"
+#include "formater.h"
+ 
+struct packet {
+	unsigned short _hardware_type;
+	unsigned short _protocol_type;
+	unsigned char _hardware_address_length;
+	unsigned char _protocol_address_length;
+	unsigned short _opcode;
+	unsigned char _src_mac[ETH_ALEN];
+	unsigned char _src_ip[4];
+	unsigned char _dest_mac[ETH_ALEN];
+	unsigned char _dest_ip[4];
+	char fill[18];
+};
+
+char *macresolvMD(char *smac, char *sip, char *dip) {
+	int sock;
+	char eth_cache[ETH_FRAME_LEN];
+	struct ethhdr *p_eth_header;
+	char eth_dest[ETH_ALEN]       = {0xFF, 0xFF, 0xFF, 0xFF, 0xFF, 0xFF};
+	char eth_dest_dummy[ETH_ALEN] = {0x00, 0x00, 0x00, 0x00, 0x00, 0x00};
+	
+	struct in_addr in, dest;
+	struct sockaddr to;
+	char buffer[65535], *final_mac = NULL, final_ip[64];
+
+	// ethernet header
+	p_eth_header = (struct ethhdr*) eth_cache;
+	memcpy(p_eth_header->h_dest, eth_dest, ETH_ALEN);
+	p_eth_header->h_proto = htons(0x0806);
+
+	// arp data
+	struct packet *p_arp, *arp_rply;
+	p_arp = (struct packet *)(eth_cache + ETH_HLEN);
+	p_arp->_hardware_type           = htons(0x1);
+	p_arp->_protocol_type           = htons (0x800);
+	p_arp->_hardware_address_length = ETH_ALEN;
+	p_arp->_protocol_address_length = 4;
+	p_arp->_opcode                  = htons(0x0001);
+
[…]

### 2014-08-25 reseau/arp-libnet/macresolv.h

@@ -1,0 +1,13 @@
+#ifndef MAC_RESOLV_H
+#define MAC_RESOLV_H
+	char *macresolvMD(char *smac, char *sip, char *dip);
+	
+	#define ETH_ALEN       6
+	#define ETH_HLEN       14
+	#define ETH_FRAME_LEN  1514
+	#define ETH_DATA_LEN   1500
+	
+	#define IP_ALEN        4
+	
+	#define INTERFACE      "eth0"
+#endif

### 2014-08-25 sgbd/http/alimcb.js

@@ -1,0 +1,130 @@
+$(document).ready(function() {
+	$.datepicker.setDefaults($.datepicker.regional["fr"]);
+	
+	$('.date').datepicker({
+		dateFormat: 'yy-mm-dd',
+	});
+});
+
+function result(data) {
+	console.log(data);
+	var table = $('#result table');
+	
+	table.empty();
+	
+	if(!data.length)
+		table.append($('<tr>').html($('<td>').html('Aucun résultat')));
+	
+	for(var i = 0; i < data.length; i++) {
+		ckbox = '<input type="checkbox" checked="checked" name="ids" value="' + data[i].id + '" />';
+		span  = '<span onclick="preview(\'' + data[i].id  + '\')">' + data[i].key + '</span>';
+		
+		table.append($('<tr>').html($('<td>').html(ckbox + ' ' + span)));
+	}
+	
+	$('#alim').css('display', 'block');
+}
+
+function mklist(items) {
+	var html = '<ul>';
+	
+	if(items.name == undefined) {	
+		for(var index in items)
+			html += '<li>' + items[index].name + '</li>';
+			
+	} else html += '<li>' + items.name + '</li>';
+	
+	html += '</ul>';
+	
+	return html;
+}
+
+function mktable(items) {
+	var html = '<table>';
+	
+	for(var index in items) {
+		html += '<tr><td>' + index + '</td><td>';
+			
+		if(typeof items[index] == 'object' && items[index] != null) {
+			html += mklist(items[index]);
+			
+		} else html += items[index];
+		
+		html += '</td>';
+	}
+	
+	html += '</table>';
+	
+	return html;
+}
+
+function preview(id) {
+	$.get('/rechci?id=' + id).done(function(data) {
+		console.log(data);
+		$.fancybox(mktable(data));
+	});
+}
+
+function ajaxsearch(root) {
+	var output = {};
+	
+	if(root.id.value) {
+		output.id = root.id.value;
+		
+	} else {
+		if(root.title.value)
+			output.title = root.title.value;
+		
+		if(root.actor.value)
+			output.actor = root.actor.value;
+			
+		if(root.director.value)
+			output.director = root.director.value;
+		
+		if(root.genre.value)
+			output.genre = root.genre.value;
+		
+		if(root.certification.value)
+			output.certification = root.certification.value;
+		
+		if(root.vote_avg_max.value)
+			output.vote_avg_max = root.vote_avg_max.value;
+		
[…]

### 2014-08-25 sgbd/http/cmdplaces.js

@@ -1,0 +1,393 @@
+var currentlist = null;
+var slots = ["", "10h", "14h", "18h", "22h"];
+var weekdays = ["Lundi", "Mardi", "Mercredi", "Jeudi", "Vendredi", "Samedi", "Dimanche"];
+var months = ["janvier", "février", "mars", "avril", "mai", "juin", "juillet", "août", "septembre", "octobre", "novembre", "décembre"];
+
+function movielist(list) {
+	console.log(list);
+	var delay = 0;
+	
+	// clearing current list
+	$('#movies ul').html('');
+	
+	for(var i = 0; i < list.length; i++) {
+		var item = list[i];
+		
+		$('#movies ul').append($('<li onclick="movieinfo(' + item.movie.id + ');">' +
+			'<div class="image">' +
+			'<img src="data:image/jpg;base64,' + item.image + '" alt="" />' +
+			'<h4><span>Pérénité: ' + item.movie.perenity.toFixed(2) + '</span><br />' + 
+			'<span>Popularité: ' + item.movie.popularity +  '</span></h4>' +
+			'<h3>' + item.movie.title + '</h3>' +
+			'</div>' +
+			'</li>'
+			
+		).hide().delay(delay).fadeIn(400));
+		
+		delay += 150;
+	}
+}
+
+function result(data) {
+	movielist(data);
+}
+
+function ajaxsearch(root) {
+	var output = {};
+	
+	if(root.title.value)
+		output.title = root.title.value;
+	
+	if(root.popularity_value.value) {
+		output.popularity_value = root.popularity_value.value;
+		output.popularity_type = root.popularity_type.value;
+	}
+		
+	if(root.perenity_value.value) {
+		output.perenity_value = root.perenity_value.value;
+		output.perenity_type = root.perenity_type.value;
+	}
+	
+	$.post('/rechplaces', output).done(result);
+			
+	return false;
+}
+
+function mklist(items) {
+	var output = '';
+	
+	for(var i = 0; i < items.length; i++) {
+		if(i > 5)
+			output += '<li style="display: none;">' + items[i] + '</li>';
+		else output += '<li>' + items[i] + '</li>';
+		
+		if(i == 5)
+			output += '<li onclick="$(this).remove(); $(\'#moreinfo ul li\').show();" style="cursor: hand;">voir plus</li>';
+	}
+	
+	return output;
+}
+
+function orderdata(data) {
[…]

### 2014-08-25 sgbd/http/rechplaces.js

@@ -1,0 +1,194 @@
+function movielist(list) {
+	console.log(list);
+	var delay = 0;
+	
+	// clearing current list
+	$('#movies ul').html('');
+	
+	for(var i = 0; i < list.length; i++) {
+		var item = list[i];
+		
+		$('#movies ul').append($('<li onclick="movieinfo(' + item.movie.id + ');">' +
+			'<div class="image">' +
+			'<img src="data:image/jpg;base64,' + item.image + '" alt="" />' +
+			'<h4><span>Pérénité: ' + item.movie.perenity.toFixed(2) + '</span><br />' + 
+			'<span>Popularité: ' + item.movie.popularity +  '</span></h4>' +
+			'<h3>' + item.movie.title + '</h3>' +
+			'</div>' +
+			'</li>'
+			
+		).hide().delay(delay).fadeIn(400));
+		
+		delay += 150;
+	}
+}
+
+function result(data) {
+	movielist(data);
+}
+
+function ajaxsearch(root) {
+	var output = {};
+	
+	if(root.title.value)
+		output.title = root.title.value;
+	
+	if(root.popularity_value.value) {
+		output.popularity_value = root.popularity_value.value;
+		output.popularity_type = root.popularity_type.value;
+	}
+		
+	if(root.perenity_value.value) {
+		output.perenity_value = root.perenity_value.value;
+		output.perenity_type = root.perenity_type.value;
+	}
+	
+	$.post('/rechplaces', output).done(result);
+			
+	return false;
+}
+
+function mklist(items) {
+	var output = '';
+	
+	for(var i = 0; i < items.length; i++) {
+		if(i > 5)
+			output += '<li style="display: none;">' + items[i] + '</li>';
+		else output += '<li>' + items[i] + '</li>';
+		
+		if(i == 5)
+			output += '<li onclick="$(this).remove(); $(\'#moreinfo ul li\').show();" style="cursor: hand;">voir plus</li>';
+	}
+	
+	return output;
+}
+
+function orderdata(data) {
+	var ordered = [{
+		day: data[0].day,
+		show: [{
+			room: data[0].room,
+			seats: data[0].seats,
+			timeslot: data[0].timeslot,
+			remain: data[0].remaining_seats
+		}]
+	}];
+	
+	for(var i = 1; i < data.length; i++) {
+		var found = 0;
+		
[…]

### 2014-08-25 sgbd/polis-alimcb.js

@@ -5,11 +5,12 @@
 // Author: Daniel Maxime, 2326
 // 
 
-var util = require('util');
-var events = require('events');
+var util    = require('util');
+var events  = require('events');
 var sqlite3 = require('./modules/sqlite3').verbose();
 var MaxuxCouchDB = require('./modules/maxux-couch/maxux-couch');
-var oracle = require("./modules/oracle");
+var oracle  = require("./modules/oracle");
+var http    = require('http');
 
 var AlimCB = function(db_file) {
 	var db = new sqlite3.Database(db_file);
@@ -20,10 +21,9 @@ var AlimCB = function(db_file) {
 	var baseurl    = '/movies/';
 	var self       = this;
 	
-	this.def_mean   = 7.5;
-	this.def_stddev = 2;
-	
-	var picture_base = 'http://cf2.imgobject.com/t/p/' + 'w185/';
+	this.def_mean     = 7.5;
+	this.def_stddev   = 2;
+	this.picture_base = 'http://cf2.imgobject.com/t/p/' + 'w185/';
 	
 	var oradata = {
 		'hostname': '10.142.1.101',
@@ -47,62 +47,151 @@ var AlimCB = function(db_file) {
 	// this should be done for each movie to transfert
 	//
 	this.process = function(movie, calling, root) {
-		console.log(movie);
+		var self      = this;
 		
-		var artists = new Array();
+		var actors    = new Array();
+		var directors = new Array();
+		var genres    = new Array();
+		var companies = new Array();
+		var languages = new Array();
+		
+		this._movie = movie;
+		
+		if(movie.data.poster_path != null)
+			this._path  = root.picture_base + movie.data.poster_path;
+			
+		else this._path = null;
+		
 		var args    = [
+			movie.data._id,
 			movie.data.title,
 			movie.data.vote_average,
 			movie.data.vote_count,
 			movie.count,
 			movie.data.overview,
 			null,
-			new Date(movie.data.release_date),
+			(movie.data.release_date != "") ? new Date(movie.data.release_date) : null,
 			(movie.data.certification == undefined) ? null : movie.data.certification,
 			movie.data.runtime,
 		];
 		
-		var stuff = 
-			"DECLARE                         " +
-			" m movies%rowtype;              " +
-			" s artists_t;                   " +
-			"BEGIN                           " +
-			"  m.title := :1;                " +
-			"  m.vote_average := :2;         " +
-			"  m.vote_count := :3;           " +
[…]

### 2014-08-25 sgbd/polis-cmdplaces-httpd.js

@@ -1,0 +1,37 @@
+//
+// Rennequinepolis
+// Static web pages server, used for web-ui
+//
+// Author: Daniel Maxime, 2326
+// 
+
+var express = require('./modules/express');
+
+//
+// load interfaces
+//
+var CmdPlaces = require('./polis-cmdplaces.js');
+cmdplaces = new CmdPlaces();
+
+//
+// provides a more complexe web server
+// which parse the query and reply from cache database
+// and give a static file access to http folder
+//
+var app = express();
+
+// static contents
+app.use(express.static('./http'));
+
+// dynamic contents
+app.use(express.bodyParser());
+
+app.post('/rechplaces', function(req, res) {
+	cmdplaces.parse(res, req.body);
+});
+
+app.post('/cmdplaces', function(req, res) {
+	cmdplaces.save(res, req.body);
+});
+
+app.listen(8080);

### 2014-08-25 sgbd/polis-cmdplaces.js

@@ -1,0 +1,326 @@
+//
+// Rennequinepolis
+// RechPlaces implementation
+//
+// Author: Daniel Maxime, 2326
+// 
+
+var util    = require('util');
+var events  = require('events');
+var oracle  = require("./modules/oracle");
+var http    = require('http');
+
+var CmdPlaces = function() {
+	var self = this;
+	events.EventEmitter.call(this);
+	
+	var oradata = {
+		'hostname': '10.142.1.101',
+		'user': 'maxux_cc1',
+		'password': 'maxux_cc1',
+		'database': 'orcl',
+	};
+	
+	this.connection = null;
+	
+	this.panic = function(response) {
+		console.log('[+] Sending error message to client...');
+		
+		response.set({'Content-Type': 'application/json'});
+		response.send(JSON.stringify({error: "error"}));
+	}
+	
+	this.reply = function(response, data) {
+		console.log('[+] Replying to client...');
+		
+		response.set({'Content-Type': 'application/json'});
+		response.send(JSON.stringify(data));
+	}
+	
+	//
+	// saving caddie
+	//
+	this.saveitem = function(_index, item, _caller) {
+		var index = _index;
+		var caller = _caller;
+		
+		self.connection.execute(
+			"CALL SGBDCC.CmdPlace(:1, :2, :3, :4, :5, :6)",
+			[
+				new Date(item.day),
+				item.room,
+				item.movie,
+				item.timeslot,
+				item.count,
+				new oracle.OutParam(oracle.OCCIINT)
+			],
+			function(error, results) {
+				console.log(error);
+				console.log(results);
+				caller.emit('commit', {key: index, value: results.returnParam});
+			}
+		);
+	};
+	
+	this.savedata = function(query, response, root) {
+		var calling = new events.EventEmitter();
+		var list = {};
+		var remain = 0;
+		
+		calling.on('commit', function(data) {
+			list[data.key] = data.value;
+			
+			if(--remain)
+				return;
+			
+			self.reply(response, list);
+		});
+		
+		for(var x in query.list)
+			remain++;
+		
+		for(var x in query.list)
+			new self.saveitem(x, query.list[x], calling);
+		
+		return calling;
+	};
+	
+	
+	//
+	// programmation information
+	//
+	this.progra = function(movie, page, response, root) {
+		var calling = new events.EventEmitter();
+		var remain = 0;
+		
+		self.connection.execute(
[…]

### 2014-08-25 sgbd/polis-progfilms.js

@@ -1,0 +1,53 @@
+//
+// Rennequinepolis
+// Static web pages server, used for web-ui
+//
+// Author: Daniel Maxime, 2326
+// 
+
+var oracle  = require("./modules/oracle");
+var express = require('./modules/express');
+
+var oradata = {
+	'hostname': '10.142.1.101',
+	'user': 'maxux_cc1',
+	'password': 'maxux_cc1',
+	'database': 'orcl',
+};
+
+var self = this;
+var connection;
+
+oracle.connect(oradata, function(error, connection) {
+	if(error) {
+		console.log(error);
+		process.exit(1);
+	}
+	
+	self.connection = connection;
+	console.log("[+] oracle: connected");
+});
+	
+var app = express();
+app.use(express.static('./http'));
+
+// dynamic contents
+app.use(express.bodyParser());
+
+app.get('/progfilms', function(req, res) {
+	res.set({'Content-Type': 'application/json'});
+	
+	var stuff = "SELECT * FROM projection p WHERE TRUNC(day) = TRUNC(CURRENT_DATE + 1)";
+	
+	self.connection.execute(stuff, [], function(err, results) {
+		if(err != undefined) {
+			console.log(err);
+			return;
+		}
+		
+		console.log(results);
+		res.send(JSON.stringify(results));
+	});
+});
+
+app.listen(8080);

### 2014-08-25 sgbd/polis-rechci.js

@@ -80,6 +80,12 @@ var RechCI = function(db_file) {
 			args.$genre = '%' + fields.genre + '%';
 		}
 		
+		if(fields.certification != undefined) {
+			var alias = root.tableappend('certification', from, where);
+			where.push(alias + '.key LIKE $certif');
+			args.$certif = '%' + fields.certification + '%';
+		}
+		
 		if(fields.vote_avg_min != undefined || fields.vote_avg_max != undefined) {
 			if(fields.vote_avg_min == undefined || isNaN(parseFloat(fields.vote_avg_min)))
 				fields.vote_avg_min = 0;

### 2014-08-25 sgbd/polis-rechplaces-httpd.js

@@ -1,0 +1,33 @@
+//
+// Rennequinepolis
+// Static web pages server, used for web-ui
+//
+// Author: Daniel Maxime, 2326
+// 
+
+var express = require('./modules/express');
+
+//
+// load interfaces
+//
+var RechPlaces = require('./polis-rechplaces.js');
+rechplaces = new RechPlaces();
+
+//
+// provides a more complexe web server
+// which parse the query and reply from cache database
+// and give a static file access to http folder
+//
+var app = express();
+
+// static contents
+app.use(express.static('./http'));
+
+// dynamic contents
+app.use(express.bodyParser());
+
+app.post('/rechplaces', function(req, res) {
+	rechplaces.parse(res, req.body);
+});
+
+app.listen(8080);

### 2014-08-25 sgbd/polis-rechplaces.js

@@ -1,0 +1,230 @@
+//
+// Rennequinepolis
+// RechPlaces implementation
+//
+// Author: Daniel Maxime, 2326
+// 
+
+var util    = require('util');
+var events  = require('events');
+var oracle  = require("./modules/oracle");
+var http    = require('http');
+
+var RechPlaces = function() {
+	var self = this;
+	events.EventEmitter.call(this);
+	
+	var oradata = {
+		'hostname': '10.142.1.101',
+		'user': 'maxux_cc1',
+		'password': 'maxux_cc1',
+		'database': 'orcl',
+	};
+	
+	this.connection = null;
+	
+	//
+	// single movie information
+	//
+	
+	this.single = function(movie, response, root) {
+		var calling = new events.EventEmitter();
+		var remain = 0;
+		
+		self.connection.execute(
+			"CALL SGBDCC.MovieInfo(:1, :2, :3, :4)",
+			[
+				movie,
+				new oracle.OutParam(oracle.OCCICURSOR),
+				new oracle.OutParam(oracle.OCCICURSOR),
+				new oracle.OutParam(oracle.OCCICURSOR)
+			],
+			function(error, results) {
+				console.log(error);
+				self.singleset(results, response);
+			}
+		);
+		
+		return calling;
+	};
+	
+	this.singleset = function(results, response) {
+		if(results == undefined) {
+			response.set({'Content-Type': 'application/json'});
+			response.send(JSON.stringify({error: "error"}));
+			return;
+		}
+		
+		console.log(results);
+		var rs = results;
+		
+		var data = {
+			movie: {
+				id: rs.returnParam[0].ID,
+				title: rs.returnParam[0].TITLE,
+				overview: rs.returnParam[0].OVERVIEW,
+				certification: rs.returnParam[0].CERTIFICATION,
+				image: rs.returnParam[0].IMAGE.toString('base64'),
+			},
+			actors: [],
+			progra: []
+		};
+		
+		for(var i = 0; i < rs.returnParam1.length; i++)
+			data.actors.push(rs.returnParam1[i].NAME);
+		
+		for(var i = 0; i < rs.returnParam2.length; i++) {
+			data.progra.push({
+				timeslot: rs.returnParam2[i].TIME_SLOT,
+				day: rs.returnParam2[i].DAY,
+				room: rs.returnParam2[i].ROOM,
+				remaining_seats: rs.returnParam2[i].REMAINING_SEATS,
[…]

### 2014-08-25 sysdis/Othello-client/src/java/gui/GameGrid.java

@@ -1,0 +1,475 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package gui;
+
+import java.awt.Color;
+import java.awt.GridLayout;
+import java.awt.event.ActionEvent;
+import java.awt.event.ActionListener;
+import javax.resource.spi.CommException;
+import javax.swing.JButton;
+import javax.swing.JOptionPane;
+import othelloclient.Communication;
+import shared.MessageProtocol;
+
+/**
+ *
+ * @author root
+ */
+class Grid {
+    String player;
+    Color color;
+    JButton button;
+}
+
+public class GameGrid extends javax.swing.JFrame {
+    Grid[][] content = new Grid[8][8];
+    Communication communication = null;
+    String username = "unknown";
+    String player2 = "";
+    public Color mycolor = Color.green;
+    Color hint = new Color(0, 128, 0);
+    boolean ingame = true;
+    
+    public int myscore = 0;
+    public int score2 = 0;
+
+    public Color getMycolor() {
+        return mycolor;
+    }
+
+    public void setMycolor(Color mycolor) {
+        this.mycolor = mycolor;
+        
+        for(int i = 0; i < 8; i++) {
+            for(int j = 0; j < 8; j++) {
+                // it's me !
+                if(content[i][j].color.equals(mycolor))
+                    content[i][j].player = username;
+                
+                // it's not me and it's not the default color
+                else if(!content[i][j].color.equals(Color.green))
+                    content[i][j].player = player2; 
+            }
+        }
+    }
+    
+    /**
+     * Creates new form GameGrid
+     */
+    public GameGrid() {
+        initComponents();
+        this.setLocationRelativeTo(null);
+        
+        for(int i = 0; i < 8; i++) {
+            for(int j = 0; j < 8; j++) {
+                content[i][j] = new Grid();
+                content[i][j].player = null;
+                content[i][j].color  = Color.green;
+                content[i][j].button = new JButton(" ");
+                
+                content[i][j].button.setName("button-" + i + "-" + j);
+                content[i][j].button.setBackground(Color.green);
+                content[i][j].button.setEnabled(false);
+                content[i][j].button.addActionListener(new ActionListener() {
+                    @Override
[…]

### 2014-08-25 sysdis/Othello-client/src/java/gui/GameList.java

@@ -1,0 +1,236 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package gui;
+
+import java.util.LinkedList;
+import java.util.List;
+import javax.swing.DefaultListModel;
+import othelloclient.Communication;
+import shared.*;
+
+/**
+ *
+ * @author root
+ */
+public class GameList extends javax.swing.JFrame {
+    Communication communication = null;
+    String username = null;
+    List<Parties> parties = null;
+    List<Integer> ids = new LinkedList<>();
+    
+    /**
+     * Creates new form GameList
+     */
+    public GameList() {
+        initComponents();
+        setLocationRelativeTo(null);
+    }
+    
+    public GameList(Communication root, String login) {
+        this();
+        communication = root;
+        username = login;
+        RefreshList();
+    }
+    
+    public void RefreshList() {
+        parties = communication.ListeParties();
+        ids.removeAll(ids);
+        
+        if(!parties.isEmpty()) {
+            UpdateList(parties);
+        }
+    }
+    
+    public void UpdateList(List<Parties> parties) {
+        DefaultListModel model = new DefaultListModel();
+        
+        if(!parties.isEmpty())
+            jList1.removeAll();    
+        
+        for(Parties partie : parties) {
+            ids.add(partie.id.intValue());
+            model.addElement(partie.name);
+        }
+        
+        if(parties.isEmpty())
+            model.addElement("No games found");
+       
+        jList1.setModel(model);
+    }
+
+    /**
+     * This method is called from within the constructor to initialize the form.
+     * WARNING: Do NOT modify this code. The content of this method is always
+     * regenerated by the Form Editor.
+     */
+    @SuppressWarnings("unchecked")
+    // <editor-fold defaultstate="collapsed" desc="Generated Code">//GEN-BEGIN:initComponents
+    private void initComponents() {
+
+        jLabel1 = new javax.swing.JLabel();
+        jScrollPane1 = new javax.swing.JScrollPane();
+        jList1 = new javax.swing.JList();
+        jButton1 = new javax.swing.JButton();
+        jButton2 = new javax.swing.JButton();
+        jButton3 = new javax.swing.JButton();
+
[…]

### 2014-08-25 sysdis/Othello-client/src/java/gui/Login.java

@@ -1,0 +1,159 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package gui;
+
+import java.util.logging.Level;
+import java.util.logging.Logger;
+import javax.jms.JMSException;
+import javax.naming.NamingException;
+import javax.swing.JOptionPane;
+import othelloclient.Communication;
+
+/**
+ *
+ * @author root
+ */
+public class Login extends javax.swing.JFrame {
+    Communication communication = null;
+    
+    /**
+     * Creates new form Login
+     */
+    public Login() {
+        initComponents();
+        jTextField1.requestFocus();
+        setLocationRelativeTo(null);
+        getRootPane().setDefaultButton(jButton1);
+    }
+    
+    public Login(Communication communication) {
+        this();
+        this.communication = communication;
+    }
+
+    /**
+     * This method is called from within the constructor to initialize the form.
+     * WARNING: Do NOT modify this code. The content of this method is always
+     * regenerated by the Form Editor.
+     */
+    @SuppressWarnings("unchecked")
+    // <editor-fold defaultstate="collapsed" desc="Generated Code">//GEN-BEGIN:initComponents
+    private void initComponents() {
+
+        jTextField1 = new javax.swing.JTextField();
+        jLabel1 = new javax.swing.JLabel();
+        jButton1 = new javax.swing.JButton();
+
+        setDefaultCloseOperation(javax.swing.WindowConstants.EXIT_ON_CLOSE);
+        setTitle("Login");
+        setResizable(false);
+        addWindowListener(new java.awt.event.WindowAdapter() {
+            public void windowClosing(java.awt.event.WindowEvent evt) {
+                formWindowClosing(evt);
+            }
+        });
+
+        jLabel1.setText("Login:");
+
+        jButton1.setText("Connexion");
+        jButton1.addActionListener(new java.awt.event.ActionListener() {
+            public void actionPerformed(java.awt.event.ActionEvent evt) {
+                jButton1ActionPerformed(evt);
+            }
+        });
+
+        javax.swing.GroupLayout layout = new javax.swing.GroupLayout(getContentPane());
+        getContentPane().setLayout(layout);
+        layout.setHorizontalGroup(
+            layout.createParallelGroup(javax.swing.GroupLayout.Alignment.LEADING)
[…]

### 2014-08-25 sysdis/Othello-client/src/java/gui/NewGame.java

@@ -1,0 +1,156 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package gui;
+
+import javax.swing.JOptionPane;
+import othelloclient.Communication;
+
+/**
+ *
+ * @author root
+ */
+public class NewGame extends javax.swing.JFrame {
+    Communication communication = null;
+    String username = "unknown";
+    
+    /**
+     * Creates new form NewGame
+     */
+    public NewGame() {
+        initComponents();
+        this.setLocationRelativeTo(null);
+        jTextField1.requestFocus();
+        getRootPane().setDefaultButton(jButton1);
+    }
+    
+    public NewGame(Communication communication, String username) {
+        this();
+        this.communication = communication;
+        this.username = username;
+    }
+
+    /**
+     * This method is called from within the constructor to initialize the form.
+     * WARNING: Do NOT modify this code. The content of this method is always
+     * regenerated by the Form Editor.
+     */
+    @SuppressWarnings("unchecked")
+    // <editor-fold defaultstate="collapsed" desc="Generated Code">//GEN-BEGIN:initComponents
+    private void initComponents() {
+
+        jButton1 = new javax.swing.JButton();
+        jLabel1 = new javax.swing.JLabel();
+        jTextField1 = new javax.swing.JTextField();
+        jCheckBox1 = new javax.swing.JCheckBox();
+
+        setDefaultCloseOperation(javax.swing.WindowConstants.DISPOSE_ON_CLOSE);
+        setResizable(false);
+
+        jButton1.setText("Créer");
+        jButton1.addActionListener(new java.awt.event.ActionListener() {
+            public void actionPerformed(java.awt.event.ActionEvent evt) {
+                jButton1ActionPerformed(evt);
+            }
+        });
+
+        jLabel1.setText("Nom de la partie:");
+
+        jCheckBox1.setText("Sauver le déroulement");
+
+        javax.swing.GroupLayout layout = new javax.swing.GroupLayout(getContentPane());
+        getContentPane().setLayout(layout);
+        layout.setHorizontalGroup(
+            layout.createParallelGroup(javax.swing.GroupLayout.Alignment.LEADING)
+            .addGroup(layout.createSequentialGroup()
+                .addContainerGap()
[…]

### 2014-08-25 sysdis/Othello-client/src/java/othelloclient/Communication.java

@@ -1,0 +1,275 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package othelloclient;
+
+import gui.GameGrid;
+import gui.GameList;
+import java.awt.Color;
+import java.io.Serializable;
+import java.util.List;
+import java.util.logging.Level;
+import java.util.logging.Logger;
+import javax.jms.Connection;
+import javax.jms.ConnectionFactory;
+import javax.jms.Destination;
+import javax.jms.JMSException;
+import javax.jms.Message;
+import javax.jms.MessageListener;
+import javax.jms.MessageProducer;
+import javax.jms.ObjectMessage;
+import javax.jms.Session;
+import javax.jms.Topic;
+import javax.jms.TopicConnection;
+import javax.jms.TopicConnectionFactory;
+import javax.jms.TopicSession;
+import javax.jms.TopicSubscriber;
+import javax.naming.Context;
+import javax.naming.InitialContext;
+import javax.naming.NamingException;
+import shared.MessageProtocol;
+import sysdis.SessionRemote;
+
+/**
+ *
+ * @author root
+ */
+public class Communication implements MessageListener {
+    private static SessionRemote session;
+    public GameGrid currentGrid = null;
+    public GameList gameList = null;
+    public String username = null;
+    public int gameid = 0;
+    public boolean save = false;
+    public int sequence = 0;
+    
+    public Communication(SessionRemote remote) {
+        session = remote;
+    }
+    
+    public void SendMessage(MessageProtocol msg) {
+        try {
+            sendJMSMessageToTopic2(msg);
+        } catch (JMSException ex) {
+            Logger.getLogger(Communication.class.getName()).log(Level.SEVERE, null, ex);
+        } catch (NamingException ex) {
+            Logger.getLogger(Communication.class.getName()).log(Level.SEVERE, null, ex);
+        }
+    }
+    
+    public boolean CheckLogin(String login) {
+        return session.CheckLogin(login);
+    }
+    
+    public String Login(String login) {
+        System.out.println("[COM] Checking username");        
+        this.username = login;
+        
+        try {
+            Messenger();
+            
+            MessageProtocol data = new MessageProtocol(gameid);
+            data.action = "HELLO";
+            data.payload = username;
+            SendMessage(data);
+            
+        } catch (NamingException ex) {
[…]

### 2014-08-25 sysdis/Othello-client/src/java/othelloclient/Main.java

@@ -1,0 +1,45 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package othelloclient;
+
+import gui.Login;
+import javax.ejb.EJB;
+import sysdis.SessionRemote;
+
+/**
+ *
+ * @author root
+ */
+public class Main {
+    @EJB
+    private static SessionRemote session;
+    
+    /**
+     * @param args the command line arguments
+     */
+    public static void main(String[] args) {
+        System.out.println("Starting client...");
+        System.out.println(session.Starter());
+        
+        //
+        // FIXME: WebServices Demo
+        //
+        if(true) {
+            new WebServicesDemo(session);
+            return;
+        }
+        //
+        //
+        //
+        
+        Communication communication = new Communication(session);
+        
+        // pop login box
+        Login login = new Login(communication);
+        login.setVisible(true);
+    }    
+}

### 2014-08-25 sysdis/Othello-client/src/java/othelloclient/WebServicesDemo.java

@@ -1,0 +1,74 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package othelloclient;
+
+import java.util.List;
+import shared.*;
+import sysdis.SessionRemote;
+
+/**
+ *
+ * @author root
+ */
+public class WebServicesDemo {
+    private static SessionRemote session;
+            
+    WebServicesDemo(SessionRemote session) {
+        this.session = session;
+        System.out.println("--- ListMyGames ---");
+        ListMyGames("user1");
+        
+        System.out.println("--- GetMyBoard ---");
+        GetMyBoard("user1");
+        
+        System.out.println("--- ListGamesFinished (true) ---");
+        ListGamesFinished(true);
+        
+        System.out.println("--- ListGamesFinished (false) ---");
+        ListGamesFinished(false);
+        
+        System.out.println("--- ListGames ---");
+        ListGames();
+        
+        System.out.println("--- GetGameById ---");
+        GetGameById(1);
+    }
+    
+    private void ListMyGames(String username) {
+        List<Parties> parties = session.WebGetMyParties(username);
+        
+        for(Parties p : parties) {
+            System.out.println(p.author + " | " + p.created + " | " + p.player2);
+        }
+    }
+    
+    private void GetMyBoard(String username) {
+        Board board = session.WebGetMyBoard(username);
+        System.out.println(board.username + " | " + board.win + " | " + board.lost + " = " + board.total);
+    }
+    
+    private void ListGamesFinished(boolean finished) {
+        List<Parties> parties = session.WebGetPartiesFinished(finished);
+        
+        for(Parties p : parties) {
+            System.out.println(p.author + " | " + p.created + " | " + p.player2);
+        }
+    }
+    
+    private void ListGames() {
+        List<Parties> parties = session.WebListParties();
+        
+        for(Parties p : parties) {
+            System.out.println(p.author + " | " + p.created + " | " + p.player2);
+        }
+    }
+    
+    private void GetGameById(int id) {
+        Parties p = session.WebGetPartieById(id);
+        System.out.println(p.author + " | " + p.created + " | " + p.player2);
+    }
+}

### 2014-08-25 sysdis/Othello-interfaces/src/shared/Board.java

@@ -1,0 +1,27 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package shared;
+
+import java.io.Serializable;
+
+/**
+ *
+ * @author root
+ */
+public class Board implements Serializable {
+    public String username;
+    public int win;
+    public int lost;
+    public int total;
+    
+    public Board(String username) {
+        this.username = username;
+        win = 0;
+        lost = 0;
+        total = 0;
+    }
+}

### 2014-08-25 sysdis/Othello-interfaces/src/shared/MessageProtocol.java

@@ -1,0 +1,47 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package shared;
+
+import java.awt.Color;
+import java.io.Serializable;
+
+/**
+ *
+ * @author root
+ */
+public class MessageProtocol implements Serializable {
+    public String source;
+    public String action;
+    public String payload;
+    public int x;
+    public int y;
+    public String player2;
+    public Color color;
+    public int gameid;
+    public int score1;
+    public int score2;
+    public boolean save;
+    
+    public MessageProtocol() {
+        source = "unknown";
+        action = "UNDEFINED";
+        payload = "";
+        
+        x = 0;
+        y = 0;
+        
+        player2 = "";
+        gameid = 0;
+        save = false;
+    }
+    
+    public MessageProtocol(int gameid) {
+        this();
+        this.gameid = gameid;
+    }
+            
+}

### 2014-08-25 sysdis/Othello-interfaces/src/shared/Parties.java

@@ -1,0 +1,27 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package shared;
+
+import java.io.Serializable;
+import java.util.Date;
+
+/**
+ *
+ * @author root
+ */
+public class Parties implements Serializable {
+    public Long id;
+    public String name;
+    public Boolean save;
+    public Boolean finished;
+    public Date created;
+    public int winner;
+    public String author;
+    public String player2;
+    public int score1;
+    public int score2;
+}

### 2014-08-25 sysdis/Othello-interfaces/src/sysdis/SessionRemote.java

@@ -1,0 +1,45 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package sysdis;
+
+import java.util.List;
+import javax.ejb.Remote;
+import shared.*;
+
+/**
+ *
+ * @author root
+ */
+@Remote
+public interface SessionRemote {
+
+    String Hello();
+
+    String Starter();
+
+    String UserLogin(String login);
+
+    List ListeParties();
+
+    void UserDisconnect(String login);
+
+    int GameCreation(String name, String username, boolean save);
+
+    Boolean CheckLogin(String login);
+
+    List<Parties> WebGetMyParties(String username);
+
+    Board WebGetMyBoard(String username);
+
+    Parties WebGetPartieById(int id);
+
+    List<Parties> WebListParties();
+
+    List<Parties> WebGetPartiesFinished(boolean finished);
+    
+    
+}

### 2014-08-25 sysdis/Othello/Othello-ejb/src/java/db/DbManager.java

@@ -1,0 +1,210 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package db;
+
+import java.util.LinkedList;
+import java.util.List;
+import javax.persistence.EntityManager;
+import javax.persistence.EntityManagerFactory;
+import javax.persistence.EntityTransaction;
+import javax.persistence.Persistence;
+import javax.transaction.Transaction;
+import shared.Board;
+import tables.*;
+
+/**
+ *
+ * @author root
+ */
+public class DbManager {
+    EntityManagerFactory emf = null;
+    EntityManager em = null;
+    
+    public DbManager() {
+        emf = Persistence.createEntityManagerFactory("Othello-ejbPU");
+        em = emf.createEntityManager();
+    }
+    
+    public EntityTransaction NewTransaction() {
+        EntityTransaction tx = em.getTransaction();
+        tx.begin();
+        
+        return tx;
+    }
+    
+    //
+    // Users
+    //
+    public String UserLogin(String login) {
+        EntityTransaction tx = NewTransaction();
+        Users user = em.find(Users.class, login);
+        
+        if(user == null) {
+            System.out.println("[DB] Not found, creating user");
+            user = new Users();
+            user.setUsername(login);
+            user.setConnected(true);
+            
+        } else {
+            System.out.println("[DB] User found");
+            System.out.println(user.getUsername());
+            user.setConnected(true);
+        }
+        
+        // save user or new state
+        em.persist(user);
+        tx.commit();
+        
+        return login;
+    }
+    
+    public void UserDisconnect(String login) {
+        EntityTransaction tx = NewTransaction();
+        Users user = em.find(Users.class, login);
+        
+        if(user != null) {
+            System.out.println("[DB] Found, setting disconnected flag");
+            user.setConnected(false);
+            em.persist(user);
+            tx.commit();
+            
+            PartiesRemoveFromAuthor(login);
+        }
+    }
+    
+    public Boolean UserCheck(String username) {
+        Users user = em.find(Users.class, username);
+        
+        if(user == null) {
+            return true;
+            
+        } else {
+            return !user.isConnected();
+        }
+    }
+    
+    //
+    // Parties
+    //
+    public List<Parties> PartiesList() {
+        return em.createNamedQuery("Parties.listWaiting").getResultList();
+    }
+    
[…]

### 2014-08-25 sysdis/Othello/Othello-ejb/src/java/sysdis/Messenger.java

@@ -1,0 +1,183 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package sysdis;
+
+import db.DbManager;
+import java.awt.Color;
+import java.util.logging.Level;
+import java.util.logging.Logger;
+import javax.annotation.Resource;
+import javax.ejb.ActivationConfigProperty;
+import javax.ejb.MessageDriven;
+import javax.inject.Inject;
+import javax.jms.JMSConnectionFactory;
+import javax.jms.JMSContext;
+import javax.jms.JMSException;
+import javax.jms.Message;
+import javax.jms.MessageListener;
+import javax.jms.ObjectMessage;
+import javax.jms.Topic;
+import shared.MessageProtocol;
+import tables.Parties;
+
+/**
+ *
+ * @author root
+ */
+@MessageDriven(activationConfig = {
+    @ActivationConfigProperty(propertyName = "clientId", propertyValue = "jms/Topic"),
+    @ActivationConfigProperty(propertyName = "destinationLookup", propertyValue = "jms/Topic"),
+    @ActivationConfigProperty(propertyName = "subscriptionDurability", propertyValue = "Durable"),
+    @ActivationConfigProperty(propertyName = "subscriptionName", propertyValue = "jms/Topic"),
+    @ActivationConfigProperty(propertyName = "destinationType", propertyValue = "javax.jms.Topic")
+})
+public class Messenger implements MessageListener {
+    @Resource(mappedName = "jms/Topic")
+    private Topic topic;
+    @Inject
+    @JMSConnectionFactory("java:comp/DefaultJMSConnectionFactory")
+    private JMSContext context;
+    DbManager db = null;
+    
+    public Messenger() {
+        db = new DbManager();
+    }
+    
+    public void GameAddUser(int partie, String username) {
+        Parties game = db.PartieUpdatePlayer(partie, username);
+        
+        // reply to user2
+        MessageProtocol data = new MessageProtocol();
+        data.source = "server";
+        data.action = "JOIN-ACK";
+        data.payload = game.getAuthor();
+        data.color = Color.white;
+        data.gameid = partie;
+        data.save = game.isSave();
+        
+        sendJMSMessageToTopic(data, username);
+        
+        // notify user1
+        data = new MessageProtocol();
+        data.source = "server";
+        data.action = "JOIN-ACK";
+        data.payload = username;
[…]

### 2014-08-25 sysdis/Othello/Othello-ejb/src/java/sysdis/Session.java

@@ -1,0 +1,148 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package sysdis;
+
+import db.DbManager;
+import java.util.LinkedList;
+import java.util.List;
+import javax.ejb.Stateless;
+import javax.persistence.EntityManager;
+import javax.persistence.EntityManagerFactory;
+import javax.persistence.EntityTransaction;
+import javax.persistence.Persistence;
+import shared.Board;
+import tables.Parties;
+
+/**
+ *
+ * @author root
+ */
+@Stateless
+public class Session implements SessionRemote {
+    DbManager db = null;
+    
+    public Session() {
+        db = new DbManager();
+    }
+    
+    @Override
+    public String Hello() {
+        return "Hello world";
+    }
+
+    @Override
+    public String Starter() {
+        return "Client connected.";
+    }
+
+    //
+    // Users
+    //
+    public String UserLogin(String login) {
+        return db.UserLogin(login);
+    }
+    
+    public void UserDisconnect(String login) {
+        System.out.println("[+] Requesting disconnection");
+        db.UserDisconnect(login);
+        System.out.println("[+] Disconnected.");
+    }
+    
+    public Boolean CheckLogin(String login) {
+        return db.UserCheck(login);
+    }
+    
+    //
+    // Parties
+    //
+    public List<shared.Parties> ListeParties() {
+        List<Parties> fromdb = db.PartiesList();
+        List<shared.Parties> toclient = new LinkedList();
+        
+        for(Parties partie : fromdb) {
+            System.out.println("[SESS] >> " + partie.getName());
+            
+            shared.Parties temp = new shared.Parties();
+            temp.id = partie.getId();
+            temp.name = partie.getName();
+            temp.created = partie.getCreated();
+            toclient.add(temp);
+        }
+        
+        return toclient;
+    }
+
+    public int GameCreation(String name, String username, boolean save) {
+        System.out.println("[SESS] Requesting new game");
+        return db.GameCreate(name, username, save);
+    }
+    
+    //
+    //
+    //
+    shared.Parties PortPartie(tables.Parties in) {
+        shared.Parties out = new shared.Parties();
+        
+        out.id = in.getId();
+        out.created = in.getCreated();
+        out.author = in.getAuthor();
+        out.player2 = in.getPlayer2();
+        out.name = in.getName();
[…]

### 2014-08-25 sysdis/Othello/Othello-ejb/src/java/sysdis/exceptions/IllegalOrphanException.java

@@ -1,0 +1,20 @@
+package sysdis.exceptions;
+
+import java.util.ArrayList;
+import java.util.List;
+
+public class IllegalOrphanException extends Exception {
+    private List<String> messages;
+    public IllegalOrphanException(List<String> messages) {
+        super((messages != null && messages.size() > 0 ? messages.get(0) : null));
+        if (messages == null) {
+            this.messages = new ArrayList<String>();
+        }
+        else {
+            this.messages = messages;
+        }
+    }
+    public List<String> getMessages() {
+        return messages;
+    }
+}

### 2014-08-25 sysdis/Othello/Othello-ejb/src/java/sysdis/exceptions/NonexistentEntityException.java

@@ -1,0 +1,10 @@
+package sysdis.exceptions;
+
+public class NonexistentEntityException extends Exception {
+    public NonexistentEntityException(String message, Throwable cause) {
+        super(message, cause);
+    }
+    public NonexistentEntityException(String message) {
+        super(message);
+    }
+}

### 2014-08-25 sysdis/Othello/Othello-ejb/src/java/sysdis/exceptions/PreexistingEntityException.java

@@ -1,0 +1,10 @@
+package sysdis.exceptions;
+
+public class PreexistingEntityException extends Exception {
+    public PreexistingEntityException(String message, Throwable cause) {
+        super(message, cause);
+    }
+    public PreexistingEntityException(String message) {
+        super(message);
+    }
+}

### 2014-08-25 sysdis/Othello/Othello-ejb/src/java/sysdis/exceptions/RollbackFailureException.java

@@ -1,0 +1,10 @@
+package sysdis.exceptions;
+
+public class RollbackFailureException extends Exception {
+    public RollbackFailureException(String message, Throwable cause) {
+        super(message, cause);
+    }
+    public RollbackFailureException(String message) {
+        super(message);
+    }
+}

### 2014-08-25 sysdis/Othello/Othello-ejb/src/java/tables/History.java

@@ -1,0 +1,97 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package tables;
+
+import java.io.Serializable;
+import javax.persistence.Entity;
+import javax.persistence.GeneratedValue;
+import javax.persistence.GenerationType;
+import javax.persistence.Id;
+import javax.persistence.Table;
+
+/**
+ *
+ * @author root
+ */
+@Entity
+@Table(name = "History")
+public class History implements Serializable {
+    private static final long serialVersionUID = 1L;
+    @Id
+    @GeneratedValue(strategy = GenerationType.AUTO)
+    private Long id;
+    private int gameid;
+    private String player;
+    private int x;
+    private int y;
+
+    public String getPlayer() {
+        return player;
+    }
+
+    public void setPlayer(String player) {
+        this.player = player;
+    }
+
+    public int getX() {
+        return x;
+    }
+
+    public void setX(int x) {
+        this.x = x;
+    }
+
+    public int getY() {
+        return y;
+    }
+
+    public void setY(int y) {
+        this.y = y;
+    }
+
+    public Long getId() {
+        return id;
+    }
+
+    public void setId(Long id) {
+        this.id = id;
+    }
+
+    @Override
+    public int hashCode() {
+        int hash = 0;
+        hash += (id != null ? id.hashCode() : 0);
+        return hash;
+    }
+
+    @Override
+    public boolean equals(Object object) {
+        // TODO: Warning - this method won't work in the case the id fields are not set
+        if (!(object instanceof History)) {
+            return false;
+        }
+        History other = (History) object;
+        if ((this.id == null && other.id != null) || (this.id != null && !this.id.equals(other.id))) {
+            return false;
+        }
+        return true;
+    }
+
+    @Override
+    public String toString() {
+        return "tables.History[ id=" + id + " ]";
+    }
+
+    public int getGameid() {
+        return gameid;
+    }
+
+    public void setGameid(int gameid) {
+        this.gameid = gameid;
+    }
+    
+}

### 2014-08-25 sysdis/Othello/Othello-ejb/src/java/tables/Links.java

@@ -1,0 +1,88 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package tables;
+
+import java.io.Serializable;
+import javax.persistence.Entity;
+import javax.persistence.GeneratedValue;
+import javax.persistence.GenerationType;
+import javax.persistence.Id;
+import javax.persistence.Table;
+
+/**
+ *
+ * @author root
+ */
+@Entity
+@Table(name = "Links")
+public class Links implements Serializable {
+    private static final long serialVersionUID = 1L;
+    @Id
+    @GeneratedValue(strategy = GenerationType.AUTO)
+    private Long id;
+    private Long pid;
+    private Long uid1;
+    private Long uid2;
+
+    public Long getPid() {
+        return pid;
+    }
+
+    public void setPid(Long pid) {
+        this.pid = pid;
+    }
+
+    public Long getUid1() {
+        return uid1;
+    }
+
+    public void setUid1(Long uid1) {
+        this.uid1 = uid1;
+    }
+
+    public Long getUid2() {
+        return uid2;
+    }
+
+    public void setUid2(Long uid2) {
+        this.uid2 = uid2;
+    }
+
+    public Long getId() {
+        return id;
+    }
+
+    public void setId(Long id) {
+        this.id = id;
+    }
+
+    @Override
+    public int hashCode() {
+        int hash = 0;
+        hash += (id != null ? id.hashCode() : 0);
+        return hash;
+    }
+
+    @Override
+    public boolean equals(Object object) {
+        // TODO: Warning - this method won't work in the case the id fields are not set
+        if (!(object instanceof Links)) {
+            return false;
+        }
+        Links other = (Links) object;
+        if ((this.id == null && other.id != null) || (this.id != null && !this.id.equals(other.id))) {
+            return false;
+        }
+        return true;
+    }
+
+    @Override
+    public String toString() {
+        return "tables.Links[ id=" + id + " ]";
+    }
+    
+}

### 2014-08-25 sysdis/Othello/Othello-ejb/src/java/tables/Parties.java

@@ -1,0 +1,196 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package tables;
+
+import java.io.Serializable;
+import java.util.Date;
+import javax.persistence.Column;
+import javax.persistence.Entity;
+import javax.persistence.GeneratedValue;
+import javax.persistence.GenerationType;
+import javax.persistence.Id;
+import javax.persistence.NamedQueries;
+import javax.persistence.NamedQuery;
+import javax.persistence.Table;
+import javax.persistence.Temporal;
+import javax.persistence.TemporalType;
+
+/**
+ *
+ * @author root
+ */
+
+@Entity
+@Table(name = "Parties")
+@NamedQueries({
+@NamedQuery(
+    name = "Parties.listWaiting",
+    query = "SELECT P FROM Parties P WHERE P.finished = false"
+),
+// delete pending game without player
+@NamedQuery(
+    name = "Parties.removeFrom",
+    query = "DELETE FROM Parties P WHERE P.author = :author AND P.finished = false AND P.player2 IS NULL"
+),
+@NamedQuery(
+    name = "Parties.listByUser",
+    query = "SELECT P FROM Parties P WHERE P.author = :username OR p.player2 = :username"
+),
+@NamedQuery(
+    name = "Parties.getBoard",
+    query = "SELECT P FROM Parties P WHERE P.author = :username OR p.player2 = :username"
+),
+@NamedQuery(
+    name = "Parties.list",
+    query = "SELECT P FROM Parties P"
+),
+@NamedQuery(
+    name = "Parties.listFinished",
+    query = "SELECT P FROM Parties P WHERE P.finished = :finished"
+)
+})
+
+public class Parties implements Serializable {
+    private static final long serialVersionUID = 1L;
+    @Id
+    @GeneratedValue(strategy = GenerationType.AUTO)
+    private Long id;
+    
+    @Column(length = 128)
+    private String name;
+    private Boolean save;
+    private Boolean finished;
+    private int winner;
+    
+    @Column(length = 128)
+    private String author;
+    @Column(length = 128)
+    private String player2;
+    
+    private int score1;
+    private int score2;
+    
+    @Temporal(TemporalType.TIMESTAMP)
+    private Date created;
+    
+    public Parties() {
+        created = new Date();
+        save = false;
+        name = "No name";
+        author = null;
[…]

### 2014-08-25 sysdis/Othello/Othello-ejb/src/java/tables/Users.java

@@ -1,0 +1,69 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package tables;
+
+import java.io.Serializable;
+import javax.persistence.Entity;
+import javax.persistence.GeneratedValue;
+import javax.persistence.GenerationType;
+import javax.persistence.Id;
+import javax.persistence.Table;
+
+/**
+ *
+ * @author root
+ */
+@Entity
+@Table(name = "Users")
+public class Users implements Serializable {
+    private static final long serialVersionUID = 1L;
+    @Id
+    private String username;
+    private Boolean connected;
+
+    @Override
+    public int hashCode() {
+        int hash = 0;
+        hash += (username != null ? username.hashCode() : 0);
+        return hash;
+    }
+
+    @Override
+    public boolean equals(Object object) {
+        // TODO: Warning - this method won't work in the case the id fields are not set
+        if (!(object instanceof Users)) {
+            return false;
+        }
+        Users other = (Users) object;
+        if ((this.username == null && other.username != null) || (this.username != null && !this.username.equals(other.username))) {
+            return false;
+        }
+        return true;
+    }
+
+    @Override
+    public String toString() {
+        return "tables.Users[ id=" + username + " ]";
+    }
+
+    public String getUsername() {
+        return username;
+    }
+
+    public void setUsername(String username) {
+        this.username = username;
+    }
+
+    public Boolean isConnected() {
+        return connected;
+    }
+
+    public void setConnected(Boolean connected) {
+        this.connected = connected;
+    }
+    
+}

### 2014-08-25 sysdis/SharedData/src/shared/Parties.java

@@ -1,0 +1,23 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package shared;
+
+import java.io.Serializable;
+import java.util.Date;
+import javax.sql.rowset.serial.SerialArray;
+
+/**
+ *
+ * @author root
+ */
+public class Parties implements Serializable {
+    public Long id;
+    public String name;
+    public Boolean save;
+    public Boolean finished;
+    public Date created;
+}

### 2015-03-11 design/petra 3/node/http/parser.js
update to last version

@@ -50,7 +50,7 @@ var Parser = function(input, remote) {
 			if('$' + data[1][i].code == id)
 				return data[1][i].value;
 		
-		console.log("[-] unknown identifier: " + id);		
+		console.log("[-] unknown identifier: " + id);
 		return 0;
 	}
 	
@@ -86,6 +86,44 @@ var Parser = function(input, remote) {
 	}
 	
 	//
+	// if's
+	//
+	function if_equals(a1, a2, label) {
+		if(a1 == a2)
+			return running('call ' + label);
+		
+		return true;
+	}
+	
+	function if_notequals(a1, a2, label) {
+		if(a1 != a2)
+			return running('call ' + label);
+		
+		return true;
+	}
+	
+	function if_gt(a1, a2, label) {
+		if(a1 > a2)
+			return running('call ' + label);
+		
+		return true;
+	}
+	
+	function if_lt(a1, a2, label) {
+		if(a1 < a2)
+			return running('call ' + label);
+		
+		return true;
+	}
+	
+	function if_modulo(a1, a2, label) {
+		if(a1 % a2)
+			return running('call ' + label);
+		
+		return true;
+	}
+	
+	//
 	// parser
 	//
 	function running(line) {		
@@ -97,7 +135,7 @@ var Parser = function(input, remote) {
 		
 		switch(words[0]) {			
 			case 'write':
-				console.log("[+] writing:" + words[1] + ", " + parseInt(words[2]));
+				console.log("[+] writing: " + words[1] + ", " + parseInt(words[2]));
 				
 				var _port = words[1].replace('$', '');
 				remote.write('write', {port: _port, value: parseInt(words[2])});
@@ -105,7 +143,7 @@ var Parser = function(input, remote) {
 			break;
 			
 			case 'sleep':
-				console.log("[+] sleeping " + words[1] + "ms");
+				console.log("[+] sleeping: " + words[1] + "ms");
 				next(parseInt(words[1]));
 				return false;
 			break;
@@ -124,21 +162,34 @@ var Parser = function(input, remote) {
 			break;
 			
 			case 'if':
-				if(words[2] != '==') {
-					console.log("[-] unknown statement: " + words[2]);
-					return true;
-				}
-				
 				var a1 = gets(words[1]);
 				var a2 = gets(words[3]);
 				
-				debug("[+] checking: " + a1 + " == " + a2);
-				
-				// if match, call label
-				if(a1 == a2)
-					return running('call ' + words[4]);
-				
[…]
